---
title: "Thesis Work"
output: html_notebook
---

# Let's load in the data and packages

```{r}
library(janitor)
library(stargazer)
library(tidyverse)
library(mice)
library(DescTools)
library(survey)
library(lmtest)
library(naniar)
library(glue)
library(haven)
```

```{r}

UNASR16 <- read_dta("P:/Refugee Data/Combined ASR/2016/2016-ASR_Public_Use_File.dta")
#View(ASR16)


UNASR17 <- read_dta("P:/Refugee Data/Combined ASR/2017/2017 ASR_Public_Use_File.dta")
#View(ASR17)


UNASR18 <- read_dta("P:/Refugee Data/Combined ASR/2018/2018 ASR_Public_Use_File.dta")
#View(ASR18)


UNASR19 <- read_dta("P:/Refugee Data/Combined ASR/2019/2019 ASR_Public_Use_File.dta")
#View(ASR19)
```

```{r}
UNASR16<-zap_labels(UNASR16)
UNASR17<-zap_labels(UNASR17)
UNASR18<-zap_labels(UNASR18)
UNASR19<-zap_labels(UNASR19)

```

I need a function to make better tables
```{r}
logit_results<-function(summary_object){
  output<-cbind.data.frame(summary_object$term, round(exp(summary_object$estimate),2), round(summary_object$p.value, 3))
  return(output)
}

```





Setting up weighted household level analysis

```{r}
UNSR16<- UNASR16[UNASR16$respondent==1,]
UNSR17<- UNASR17[UNASR17$respondent==1,]
UNSR18<- UNASR18[UNASR18$respondent==1,]
UNSR19<- UNASR19[UNASR19$respondent==1,]
match("Weight_household_R1", names(UNSR16))
match("Weight_household_R27", names(UNSR16))

match("Weight_household", names(UNSR16))



```

# Cleaning and Making Variables

## Making Time till First job

```{r}
#Making the Time to Job in years variable

UNSR16$WHENJOB<-UNSR16$qn18dyear

UNSR17$WHENJOB<-UNSR17$qn18dyear

UNSR18$WHENJOB<-UNSR18$qn18dyear

UNSR19$WHENJOB<-UNSR19$qn18dyear
UNSR16$WHENJOB<- ifelse(is.na(UNSR16$qn18dyear), 0, UNSR16$qn18dyear)
UNSR17$WHENJOB<- ifelse(is.na(UNSR17$qn18dyear), 0, UNSR17$qn18dyear)
UNSR18$WHENJOB<- ifelse(is.na(UNSR18$qn18dyear), 0, UNSR18$qn18dyear)
UNSR19$WHENJOB<- ifelse(is.na(UNSR19$qn18dyear), 0, UNSR19$qn18dyear)
summary(UNSR16$qn18dyear)


# Making the RESIDENCY Variable
UNSR16$RESIDENCY<-2016-as.numeric(UNSR16$qn1jyear)
UNSR17$RESIDENCY<-2017-as.numeric(UNSR17$qn1jyear)
UNSR18$RESIDENCY<-2018-as.numeric(UNSR18$qn1jyear)
UNSR19$RESIDENCY<-2019-as.numeric(UNSR19$qn1jyear)

#Makingthe When Arrive variable
UNSR16$WHENARRIVE<-as.numeric(UNSR16$qn1jyear)
UNSR17$WHENARRIVE<-as.numeric(UNSR17$qn1jyear)
UNSR18$WHENARRIVE<-as.numeric(UNSR18$qn1jyear)
UNSR19$WHENARRIVE<-as.numeric(UNSR19$qn1jyear)

```


## Making Economic Self-Sufficiency

```{r}
UNSR16$FI<- ifelse(UNSR16$ui_soi_pubassist==999, NA, ifelse(UNSR16$ui_soi_pubassist==1, 0,1))
UNSR17$FI<- ifelse(UNSR17$ui_soi_pubassist==999, NA, ifelse(UNSR17$ui_soi_pubassist==1, 0,1))
UNSR18$FI<- ifelse(UNSR18$ui_soi_pubassist==999, NA, ifelse(UNSR18$ui_soi_pubassist==1, 0,1))
UNSR19$FI<- ifelse(UNSR19$ui_soi_pubassist==999, NA, ifelse(UNSR19$ui_soi_pubassist==1, 0,1))

table(UNSR16$FI)
```


## Making Weekly Working Hours

```{r}
UNSR16$qn6a<- ifelse(UNSR16$qn6a==98 | UNSR16$qn6a==99, NA, UNSR16$qn6a)
UNSR16$qn6b<- ifelse(UNSR16$qn6b==98 | UNSR16$qn6b==99, NA, UNSR16$qn6b)

UNSR17$qn6a<- ifelse(UNSR17$qn6a==98 | UNSR17$qn6a==99, NA, UNSR17$qn6a)
UNSR17$qn6b<- ifelse(UNSR17$qn6b==98 | UNSR17$qn6b==99, NA, UNSR17$qn6b)

UNSR18$qn6a<- ifelse(UNSR18$qn6a==98 | UNSR18$qn6a==99, NA, UNSR18$qn6a)
UNSR18$qn6b<- ifelse(UNSR18$qn6b==98 | UNSR18$qn6b==99, NA, UNSR18$qn6b)

UNSR19$qn6a<- ifelse(UNSR19$qn6a==98 | UNSR19$qn6a==99, NA, UNSR19$qn6a)
UNSR19$qn6b<- ifelse(UNSR19$qn6b==98 | UNSR19$qn6b==99, NA, UNSR19$qn6b)

summary(UNSR16$qn6b)
UNSR16$WEEKHOUR<- UNSR16$qn6b
UNSR16$WEEKHOUR<- ifelse(is.na(UNSR16$WEEKHOUR), UNSR16$qn6a, UNSR16$qn6b)

UNSR17$WEEKHOUR<- UNSR17$qn6b
UNSR17$WEEKHOUR<- ifelse(is.na(UNSR17$WEEKHOUR), UNSR17$qn6a, UNSR17$qn6b)

UNSR18$WEEKHOUR<- UNSR18$qn6b
UNSR18$WEEKHOUR<- ifelse(is.na(UNSR18$WEEKHOUR), UNSR18$qn6a, UNSR18$qn6b)

UNSR19$WEEKHOUR<- UNSR19$qn6b
UNSR19$WEEKHOUR<- ifelse(is.na(UNSR19$WEEKHOUR), UNSR19$qn6a, UNSR19$qn6b)
summary(UNSR16$WEEKHOUR)
```
## Making EDUC (Years of Education)
```{r}
UNSR16$EDUC<-ifelse(UNSR16$qn2a==99| UNSR16$qn2a==98, NA, UNSR16$qn2a)

UNSR17$EDUC<-ifelse(UNSR17$qn2a==99| UNSR17$qn2a==98, NA, UNSR17$qn2a)

UNSR18$EDUC<-ifelse(UNSR18$qn2a==99| UNSR18$qn2a==98, NA, UNSR18$qn2a)

UNSR19$EDUC<-ifelse(UNSR19$qn2a==99| UNSR19$qn2a==98, NA, UNSR19$qn2a)

```

## Making Pre-Displacement Economic Sector 1=Professional, 2= Sales, 3= Service, 4=Blue Collar, 5= STudent, 6=Other, 0=None
```{r}
UNSR16$qn3b<- ifelse(UNSR16$qn3b==98|UNSR16$qn3b== 99, NA, UNSR16$qn3b)

UNSR17$qn3b<- ifelse(UNSR17$qn3b==98|UNSR17$qn3b== 99, NA, UNSR17$qn3b)


UNSR18$qn3b<- ifelse(UNSR18$qn3b==98|UNSR18$qn3b== 99, NA, UNSR18$qn3b)

UNSR19$qn3b<- ifelse(UNSR19$qn3b==98|UNSR19$qn3b== 99, NA, UNSR19$qn3b)

##2016
# Buissness Owner, Professional, management, and white collar will be a "Professional"
UNSR16$ECOSECTOR<- ifelse(UNSR16$qn3b == 1| UNSR16$qn3b == 2|UNSR16$qn3b ==3|UNSR16$qn3b ==4|UNSR16$qn3b ==5, 1, 
      #Sales will be Sales                    
                  ifelse(UNSR16$qn3b ==6, 2, 
                          #Hospitality, service workers, and laborers will be "Service"       
                                 ifelse(UNSR16$qn3b ==9|UNSR16$qn3b ==10|UNSR16$qn3b ==11, 3, 
                                        #Skilled Trades will be "Blue Collar"
                                        ifelse(UNSR16$qn3b ==7|UNSR16$qn3b ==8|UNSR16$qn3b ==12, 4, 
                 #None is none
                 ifelse(UNSR16$qn3b ==96, 0, 
                        #Students are students
                        ifelse(UNSR16$qn3b ==13, 5, 
                 #Other is other
                 ifelse(UNSR16$qn3b== 97, 6, UNSR16$qn3b)))))))
##2017
UNSR17$ECOSECTOR<- ifelse(UNSR17$qn3b == 1| UNSR17$qn3b == 2|UNSR17$qn3b ==3|UNSR17$qn3b ==4|UNSR17$qn3b ==5, 1, 
                          
                          ifelse(UNSR17$qn3b ==6, 2, 
                                 
                                 ifelse(UNSR17$qn3b ==9|UNSR17$qn3b ==10|UNSR17$qn3b ==11, 3, 
                                        
                                        ifelse(UNSR17$qn3b ==7|UNSR17$qn3b ==8|UNSR17$qn3b ==12, 4, 
                                               ifelse(UNSR17$qn3b ==96, 0, ifelse(UNSR17$qn3b ==13, 5, 
                                                                                  ifelse(UNSR17$qn3b== 97, 6, UNSR17$qn3b)))))))
##2018
UNSR18$ECOSECTOR<- ifelse(UNSR18$qn3b == 1| UNSR18$qn3b == 2|UNSR18$qn3b ==3|UNSR18$qn3b ==4|UNSR18$qn3b ==5, 1, 
                          
                          ifelse(UNSR18$qn3b ==6, 2, 
                                 
                                 ifelse(UNSR18$qn3b ==9|UNSR18$qn3b ==10|UNSR18$qn3b ==11, 3, 
                                        
                                        ifelse(UNSR18$qn3b ==7|UNSR18$qn3b ==8|UNSR18$qn3b ==12, 4, 
                                               ifelse(UNSR18$qn3b ==96, 0, ifelse(UNSR18$qn3b ==13, 5, 
                                                                                  ifelse(UNSR18$qn3b== 97, 6, UNSR18$qn3b)))))))

#2018 is a weird year and the User's Guide backs that up. Look like they did the same thing for 2019

##2019
UNSR19<- UNSR19%>% mutate(ECOSECTOR= case_when(qn3b>=1 & qn3b <=5~1,
                                               qn3b==6~2, 
                                               qn3b==9:11~3,
                                        qn3b==7:8|qn3b==12~4,
                                        qn3b==13~5, 
                                        qn3b==97~6))

#Factorizing, Make Other the reference because 18 and 19 are all "other"
UNSR16$ECOSECTOR<- factor(UNSR16$ECOSECTOR, levels = c(0:6), labels = c("None","Professional", "Sales", "Service", "Blue Collar", "Student", "Other"))

UNSR17$ECOSECTOR<- factor(UNSR17$ECOSECTOR, levels = c(0:6), labels = c("None","Professional", "Sales", "Service", "Blue Collar", "Student", "Other"))

UNSR18$ECOSECTOR<- factor(UNSR18$ECOSECTOR, levels = c(0:6), labels = c("None","Professional", "Sales", "Service", "Blue Collar", "Student", "Other"))

UNSR19$ECOSECTOR<- factor(UNSR19$ECOSECTOR, levels = c(0:6), labels = c("None","Professional", "Sales", "Service", "Blue Collar", "Student", "Other"))

UNSR16$ECOSECTOR<-relevel(UNSR16$ECOSECTOR, ref ="Other")
UNSR17$ECOSECTOR<-relevel(UNSR17$ECOSECTOR, ref ="Other")
UNSR18$ECOSECTOR<-relevel(UNSR18$ECOSECTOR, ref ="Other")
UNSR19$ECOSECTOR<-relevel(UNSR19$ECOSECTOR, ref ="Other")
```


###Making a current economic sector variable 1=Blue Collar 2= Retail/Service, 3= Professional/Health/Ed/SocialServices, 4= General Logistics:Transport, Maintenance, General Products and Goods. 5= Other, 0=None
```{r}
#2016
#missing
UNSR16$URECOSEC<-ifelse(UNSR16$qn19b==99|UNSR16$qn19b==98,NA,
                        #Blue Collar
                        ifelse(UNSR16$qn19b==1|UNSR16$qn19b==8|UNSR16$qn19b==10, 1, 
                               
                  #Retail/Service
                  
                   ifelse(UNSR16$qn19b==2|UNSR16$qn19b==5|UNSR16$qn19b==7|UNSR16$qn19b==11, 2, 
                             ifelse(UNSR16$qn19b==4|UNSR16$qn19b==3, 3, 
                                    
                                    #General logistics
                                    
                                  ifelse(UNSR16$qn19b==9|UNSR16$qn19b==6|UNSR16$qn19b==12, 4, 
                                           ifelse(UNSR16$qn19b==97, 5 ,
                                                  ifelse(UNSR16$qn19b==96, 0,UNSR16$qn19b)))))))
#Factorize
UNSR16$URECOSEC<- factor(UNSR16$URECOSEC, labels= c("None", "BlueCollar", "Retail/Sales", "Professional/ED/Health/SocialServices", "General Logistical Support", "Other"), levels = c(0:5), ordered = F)
summary(UNSR16$URECOSEC)
table(UNSR16$URECOSEC, UNSR16$qn19b)
#2017
UNSR17$URECOSEC<-ifelse(UNSR17$qn19b==99|UNSR17$qn19b==98,NA,
                        #Blue Collar
                        ifelse(UNSR17$qn19b==1|UNSR17$qn19b==8|UNSR17$qn19b==10, 1, 
                               
                  #Retail/Service
                  
                   ifelse(UNSR17$qn19b==2|UNSR17$qn19b==5|UNSR17$qn19b==7|UNSR17$qn19b==11, 2, 
                             ifelse(UNSR17$qn19b==4|UNSR17$qn19b==3, 3, 
                                    
                                    #General logistics
                                    
                                  ifelse(UNSR17$qn19b==9|UNSR17$qn19b==6|UNSR17$qn19b==12, 4, 
                                           ifelse(UNSR17$qn19b==97, 5 ,
                                                  ifelse(UNSR17$qn19b==96, 0,UNSR17$qn19b)))))))
summary(UNSR17$URECOSEC)

#Factorize
UNSR17$URECOSEC<- factor(UNSR17$URECOSEC, labels= c("None", "BlueCollar", "Retail/Sales", "Professional/ED/Health/SocialServices", "General Logistical Support", "Other"), levels = c(0:5), ordered = F)

#2018
UNSR18$URECOSEC<-ifelse(UNSR18$qn19b==99|UNSR18$qn19b==98,NA,
                        #Blue Collar
                        ifelse(UNSR18$qn19b==1|UNSR18$qn19b==8|UNSR18$qn19b==10, 1, 
                               
                  #Retail/Service
                  
                   ifelse(UNSR18$qn19b==2|UNSR18$qn19b==5|UNSR18$qn19b==7|UNSR18$qn19b==11, 2, 
                             ifelse(UNSR18$qn19b==4|UNSR18$qn19b==3, 3, 
                                    
                                    #General logistics
                                    
                                  ifelse(UNSR18$qn19b==9|UNSR18$qn19b==6|UNSR18$qn19b==12, 4, 
                                           ifelse(UNSR18$qn19b==97, 5 ,
                                                  ifelse(UNSR18$qn19b==96, 0,UNSR18$qn19b)))))))
#Factorize
UNSR18$URECOSEC<- factor(UNSR18$URECOSEC, labels= c("None", "BlueCollar", "Retail/Sales", "Professional/ED/Health/SocialServices", "General Logistical Support", "Other"), levels = c(0:5), ordered = F)


#2019
UNSR19$URECOSEC<-ifelse(UNSR19$qn19b==99|UNSR19$qn19b==98,NA,
                        #Blue Collar
                        ifelse(UNSR19$qn19b==1|UNSR19$qn19b==8|UNSR19$qn19b==10, 1, 
                               
                  #Retail/Service
                  
                   ifelse(UNSR19$qn19b==2|UNSR19$qn19b==5|UNSR19$qn19b==7|UNSR19$qn19b==11, 2, 
                             ifelse(UNSR19$qn19b==4|UNSR19$qn19b==3, 3, 
                                    
                                    #General logistics
                                    
                                  ifelse(UNSR19$qn19b==9|UNSR19$qn19b==6|UNSR19$qn19b==12, 4, 
                                           ifelse(UNSR19$qn19b==97, 5 ,
                                                  ifelse(UNSR19$qn19b==96, 0,UNSR19$qn19b)))))))
#Factorize
UNSR19$URECOSEC<- factor(UNSR19$URECOSEC, labels= c("None", "BlueCollar", "Retail/Sales", "Professional/ED/Health/SocialServices", "General Logistical Support", "Other"), levels = c(0:5), ordered = F)
```




```{r}
#Cleaning Birth Country variable

#This clumps up every places with a n<100 in the other category
UNSR16<- UNSR16%>% mutate(ORIGIN =case_when(qn1g==1|qn1g==4|qn1g==7|qn1g==11|qn1g==12|qn1g==13|qn1g==15|qn1g==19|qn1g==21| qn1g==24| qn1g==25~97, 
                                            qn1g==96|qn1g==98|qn1g==99~NA, 
                                            .default = qn1g))

UNSR17<- UNSR17%>% mutate(ORIGIN =case_when(qn1g==1|qn1g==4|qn1g==7|qn1g==11|qn1g==12|qn1g==13|qn1g==15|qn1g==19|qn1g==21| qn1g==24| qn1g==25~97,
                                            .default = qn1g))

UNSR18<- UNSR18%>% mutate(ORIGIN =case_when(qn1g==1|qn1g==4|qn1g==7|qn1g==11|qn1g==12|qn1g==13|qn1g==15|qn1g==19|qn1g==21| qn1g==24| qn1g==25~97,
                                            .default = qn1g))

UNSR19<- UNSR19%>% mutate(ORIGIN =case_when(qn1g==1|qn1g==4|qn1g==7|qn1g==11|qn1g==12|qn1g==13|qn1g==15|qn1g==19|qn1g==21| qn1g==24| qn1g==25~97,
                                            .default = qn1g))


table(UNSR16$ORIGIN, UNSR16$qn1g)
#Make Origin a Factor with labels
summary(UNSR16$ORIGIN)

UNSR16$ORIGIN<- factor(UNSR16$ORIGIN, levels = c(2:3,5:6,9:10, 16, 18,20, 22,26, 97), labels = c("Bhutan", "Burma", "Cuba", "DR Congo", "Iran", "Iraq",  "Somalia", "Syria", "Thailand", "Ukraine", "El Salvador", "Other"))

#UNSR16$ORIGIN<- factor(UNSR16$ORIGIN,levels = c(1:22,24:26, 97), labels = c("Afghanistan", "Bhutan", "Burma","Burundi", "Cuba", "DR Congo", "Eritrea", "Ethiopia", "Iran", "Iraq", "Jordan", "Kenya", "Malaysia", "Nepal", "Rwanada", "Somalia", "Sudan", "Syria", "Tanzania", "Thailand", "Uganda",  "Ukraine", "U.S.", "Colombia", "El Salvador", "Other"))

UNSR17$ORIGIN<- factor(UNSR17$ORIGIN, levels = c(2:3,5:6,9:10, 16, 18,20, 22,26, 97), labels = c("Bhutan", "Burma", "Cuba", "DR Congo", "Iran", "Iraq",  "Somalia", "Syria", "Thailand", "Ukraine", "El Salvador", "Other"))

#UNSR17$ORIGIN<- factor(UNSR17$ORIGIN, levels = c(1:22,24:26, 97), labels = c("Afghanistan", "Bhutan", "Burma","Burundi", "Cuba", "DR Congo", "Eritrea", "Ethiopia", "Iran", "Iraq", "Jordan", "Kenya", "Malaysia", "Nepal", "Rwanada", "Somalia", "Sudan", "Syria", "Tanzania", "Thailand", "Uganda",  "Ukraine", "U.S.", "Colombia", "El Salvador", "Other"))

UNSR18$ORIGIN<- factor(UNSR18$ORIGIN, levels = c(2:3,5:6,9:10, 16, 18,20, 22,26, 97), labels = c("Bhutan", "Burma", "Cuba", "DR Congo", "Iran", "Iraq",  "Somalia", "Syria", "Thailand", "Ukraine", "El Salvador", "Other"))

#UNSR18$ORIGIN<- factor(UNSR18$ORIGIN, levels = c(1:22,24:26, 97), labels = c("Afghanistan", "Bhutan", "Burma","Burundi", "Cuba", "DR Congo", "Eritrea", "Ethiopia", "Iran", "Iraq", "Jordan", "Kenya", "Malaysia", "Nepal", "Rwanada", "Somalia", "Sudan", "Syria", "Tanzania", "Thailand", "Uganda",  "Ukraine", "U.S.", "Colombia", "El Salvador", "Other"))

UNSR19$ORIGIN<- factor(UNSR19$ORIGIN, levels = c(2:3,5:6,9:10, 16, 18,20, 22,26, 97), labels = c("Bhutan", "Burma", "Cuba", "DR Congo", "Iran", "Iraq",  "Somalia", "Syria", "Thailand", "Ukraine", "El Salvador", "Other"))

#UNSR19$ORIGIN<- factor(UNSR19$ORIGIN, levels = c(1:22,24:26, 97), labels = c("Afghanistan", "Bhutan", "Burma","Burundi", "Cuba", "DR Congo", "Eritrea", "Ethiopia", "Iran", "Iraq", "Jordan", "Kenya", "Malaysia", "Nepal", "Rwanada", "Somalia", "Sudan", "Syria", "Tanzania", "Thailand", "Uganda",  "Ukraine", "U.S.", "Colombia", "El Salvador", "Other"))

UNSR16$ORIGIN<-relevel(UNSR16$ORIGIN,ref = "Cuba")
UNSR17$ORIGIN<-relevel(UNSR17$ORIGIN,ref = "Cuba")
UNSR18$ORIGIN <-relevel(UNSR18$ORIGIN,ref = "Cuba")
UNSR19$ORIGIN <-relevel(UNSR19$ORIGIN,ref = "Cuba")
summary(UNSR19$ORIGIN)
table(UNSR19$ORIGIN, UNSR19$qn1g)
```

##Contextual Attainment

### Making country specific variance estimates. All estimates use the UN Development Program Human Development report for 2015 or the most recently available data (for Somalia): https://hdr.undp.org/en/indicators/103006. These are just raw deviations from the mean. 
```{r}
#Bhutan Mean for 2015 Mean =3.4 
UNSR16$CONTEXT<- ifelse(UNSR16$ORIGIN== "Afghanistan", UNSR16$EDUC-2.37, 
                        ifelse(UNSR16$ORIGIN== "Bhutan", UNSR16$EDUC-3.4, 
                        ifelse(UNSR16$ORIGIN=="Burma", UNSR16$EDUC-4.9, ifelse(UNSR16$ORIGIN=="Burundi", UNSR16$EDUC-2.29,
                              ifelse(UNSR16$ORIGIN=="Cuba", UNSR16$EDUC-11.4,
                                      ifelse(UNSR16$ORIGIN=="DR Congo", UNSR16$EDUC-6.4,
                                             ifelse(UNSR16$ORIGIN=="Eritrea", UNSR16$EDUC-3.9,
                                                    ifelse(UNSR16$ORIGIN=="Ethiopia", UNSR16$EDUC-2.58,
                                                    ifelse(UNSR16$ORIGIN=="Iran", UNSR16$EDUC-9.9, 
                                                           ifelse(UNSR16$ORIGIN=="Iraq", UNSR16$EDUC-6.8, ifelse(UNSR16$ORIGIN=="Jordan", UNSR16$EDUC-10.07,ifelse(UNSR16$ORIGIN=="Kenya", UNSR16$EDUC-6.3, ifelse(UNSR16$ORIGIN=="Malaysia", UNSR16$EDUC-10.23, ifelse(UNSR16$ORIGIN=="Nepal", UNSR16$EDUC-4.5, ifelse(UNSR16$ORIGIN=="Rwanada", UNSR16$EDUC-4.13,
                                                                  ifelse(UNSR16$ORIGIN=="Somalia", UNSR16$EDUC-2.1, ifelse(UNSR16$ORIGIN=="Sudan", UNSR16$EDUC-3.62,
                                                                         ifelse(UNSR16$ORIGIN=="Syria", UNSR16$EDUC-5.1, ifelse(UNSR16$ORIGIN=="Tanzania", UNSR16$EDUC-5.83, ifelse(UNSR16$ORIGIN=="Thailand", UNSR16$EDUC-8.18, ifelse(UNSR16$ORIGIN=="Uganda", UNSR16$EDUC-5.51,
                                                                              ifelse(UNSR16$ORIGIN=="Ukraine", UNSR16$EDUC-11.4, 
                                                                                       ifelse(UNSR16$ORIGIN=="U.S.", UNSR16$EDUC-13.3,ifelse(UNSR16$ORIGIN=="Colombia", UNSR16$EDUC-8.05, ifelse(UNSR16$ORIGIN=="El Salvador", UNSR16$EDUC-6.62, NA)))))))))))))))))))))))))

#2017

UNSR17$CONTEXT<- ifelse(UNSR17$ORIGIN== "Afghanistan", UNSR17$EDUC-2.37, 
                        ifelse(UNSR17$ORIGIN== "Bhutan", UNSR17$EDUC-3.4, 
                        ifelse(UNSR17$ORIGIN=="Burma", UNSR17$EDUC-4.9, ifelse(UNSR17$ORIGIN=="Burundi", UNSR17$EDUC-2.29,
                              ifelse(UNSR17$ORIGIN=="Cuba", UNSR17$EDUC-11.4,
                                      ifelse(UNSR17$ORIGIN=="DR Congo", UNSR17$EDUC-6.4,
                                             ifelse(UNSR17$ORIGIN=="Eritrea", UNSR17$EDUC-3.9,
                                                    ifelse(UNSR17$ORIGIN=="Ethiopia", UNSR17$EDUC-2.58,
                                                    ifelse(UNSR17$ORIGIN=="Iran", UNSR17$EDUC-9.9, 
                                                           ifelse(UNSR17$ORIGIN=="Iraq", UNSR17$EDUC-6.8, ifelse(UNSR17$ORIGIN=="Jordan", UNSR17$EDUC-10.07,ifelse(UNSR17$ORIGIN=="Kenya", UNSR17$EDUC-6.3, ifelse(UNSR17$ORIGIN=="Malaysia", UNSR17$EDUC-10.23, ifelse(UNSR17$ORIGIN=="Nepal", UNSR17$EDUC-4.5, ifelse(UNSR17$ORIGIN=="Rwanada", UNSR17$EDUC-4.13,
                                                                  ifelse(UNSR17$ORIGIN=="Somalia", UNSR17$EDUC-2.1, ifelse(UNSR17$ORIGIN=="Sudan", UNSR17$EDUC-3.62,
                                                                         ifelse(UNSR17$ORIGIN=="Syria", UNSR17$EDUC-5.1, ifelse(UNSR17$ORIGIN=="Tanzania", UNSR17$EDUC-5.83, ifelse(UNSR17$ORIGIN=="Thailand", UNSR17$EDUC-8.18, ifelse(UNSR17$ORIGIN=="Uganda", UNSR17$EDUC-5.51,
                                                                              ifelse(UNSR17$ORIGIN=="Ukraine", UNSR17$EDUC-11.4, 
                                                                                       ifelse(UNSR17$ORIGIN=="U.S.", UNSR17$EDUC-13.3,ifelse(UNSR17$ORIGIN=="Colombia", UNSR17$EDUC-8.05, ifelse(UNSR17$ORIGIN=="El Salvador", UNSR17$EDUC-6.62, NA)))))))))))))))))))))))))

#2018

UNSR18$CONTEXT<- ifelse(UNSR18$ORIGIN== "Afghanistan", UNSR18$EDUC-2.37, 
                        ifelse(UNSR18$ORIGIN== "Bhutan", UNSR18$EDUC-3.4, 
                        ifelse(UNSR18$ORIGIN=="Burma", UNSR18$EDUC-4.9, ifelse(UNSR18$ORIGIN=="Burundi", UNSR18$EDUC-2.29,
                              ifelse(UNSR18$ORIGIN=="Cuba", UNSR18$EDUC-11.4,
                                      ifelse(UNSR18$ORIGIN=="DR Congo", UNSR18$EDUC-6.4,
                                             ifelse(UNSR18$ORIGIN=="Eritrea", UNSR18$EDUC-3.9,
                                                    ifelse(UNSR18$ORIGIN=="Ethiopia", UNSR18$EDUC-2.58,
                                                    ifelse(UNSR18$ORIGIN=="Iran", UNSR18$EDUC-9.9, 
                                                           ifelse(UNSR18$ORIGIN=="Iraq", UNSR18$EDUC-6.8, ifelse(UNSR18$ORIGIN=="Jordan", UNSR18$EDUC-10.07,ifelse(UNSR18$ORIGIN=="Kenya", UNSR18$EDUC-6.3, ifelse(UNSR18$ORIGIN=="Malaysia", UNSR18$EDUC-10.23, ifelse(UNSR18$ORIGIN=="Nepal", UNSR18$EDUC-4.5, ifelse(UNSR18$ORIGIN=="Rwanada", UNSR18$EDUC-4.13,
                                                                  ifelse(UNSR18$ORIGIN=="Somalia", UNSR18$EDUC-2.1, ifelse(UNSR18$ORIGIN=="Sudan", UNSR18$EDUC-3.62,
                                                                         ifelse(UNSR18$ORIGIN=="Syria", UNSR18$EDUC-5.1, ifelse(UNSR18$ORIGIN=="Tanzania", UNSR18$EDUC-5.83, ifelse(UNSR18$ORIGIN=="Thailand", UNSR18$EDUC-8.18, ifelse(UNSR18$ORIGIN=="Uganda", UNSR18$EDUC-5.51,
                                                                              ifelse(UNSR18$ORIGIN=="Ukraine", UNSR18$EDUC-11.4, 
                                                                                       ifelse(UNSR18$ORIGIN=="U.S.", UNSR18$EDUC-13.3,ifelse(UNSR18$ORIGIN=="Colombia", UNSR18$EDUC-8.05, ifelse(UNSR18$ORIGIN=="El Salvador", UNSR18$EDUC-6.62, NA)))))))))))))))))))))))))

#2019

UNSR19$CONTEXT<- ifelse(UNSR19$ORIGIN== "Afghanistan", UNSR19$EDUC-2.37, 
                        ifelse(UNSR19$ORIGIN== "Bhutan", UNSR19$EDUC-3.4, 
                        ifelse(UNSR19$ORIGIN=="Burma", UNSR19$EDUC-4.9, ifelse(UNSR19$ORIGIN=="Burundi", UNSR19$EDUC-2.29,
                              ifelse(UNSR19$ORIGIN=="Cuba", UNSR19$EDUC-11.4,
                                      ifelse(UNSR19$ORIGIN=="DR Congo", UNSR19$EDUC-6.4,
                                             ifelse(UNSR19$ORIGIN=="Eritrea", UNSR19$EDUC-3.9,
                                                    ifelse(UNSR19$ORIGIN=="Ethiopia", UNSR19$EDUC-2.58,
                                                    ifelse(UNSR19$ORIGIN=="Iran", UNSR19$EDUC-9.9, 
                                                           ifelse(UNSR19$ORIGIN=="Iraq", UNSR19$EDUC-6.8, ifelse(UNSR19$ORIGIN=="Jordan", UNSR19$EDUC-10.07,ifelse(UNSR19$ORIGIN=="Kenya", UNSR19$EDUC-6.3, ifelse(UNSR19$ORIGIN=="Malaysia", UNSR19$EDUC-10.23, ifelse(UNSR19$ORIGIN=="Nepal", UNSR19$EDUC-4.5, ifelse(UNSR19$ORIGIN=="Rwanada", UNSR19$EDUC-4.13,
                                                                  ifelse(UNSR19$ORIGIN=="Somalia", UNSR19$EDUC-2.1, ifelse(UNSR19$ORIGIN=="Sudan", UNSR19$EDUC-3.62,
                                                                         ifelse(UNSR19$ORIGIN=="Syria", UNSR19$EDUC-5.1, ifelse(UNSR19$ORIGIN=="Tanzania", UNSR19$EDUC-5.83, ifelse(UNSR19$ORIGIN=="Thailand", UNSR19$EDUC-8.18, ifelse(UNSR19$ORIGIN=="Uganda", UNSR19$EDUC-5.51,
                                                                              ifelse(UNSR19$ORIGIN=="Ukraine", UNSR19$EDUC-11.4, 
                                                                                       ifelse(UNSR19$ORIGIN=="U.S.", UNSR19$EDUC-13.3,ifelse(UNSR19$ORIGIN=="Colombia", UNSR19$EDUC-8.05, ifelse(UNSR19$ORIGIN=="El Salvador", UNSR19$EDUC-6.62, NA)))))))))))))))))))))))))
summary(UNSR17$CONTEXT)
summary(UNSR18$CONTEXT)
summary(UNSR19$CONTEXT)
```

## Pre-Migration English proficiency
```{r}
UNSR16$qn4a<- ifelse(UNSR16$qn4a== 8|UNSR16$qn4a==9, NA, UNSR16$qn4a)
UNSR16$PREENG<- abs(UNSR16$qn4a-5)
Freq(UNSR16$PREENG)
UNSR16$PREENG<- factor(UNSR16$PREENG,levels = c(1,2,3,4), labels = c("Not at all", "Not Well", "Well", "Very Well"))
UNSR17$qn4a<- ifelse(UNSR17$qn4a== 8|UNSR17$qn4a==9, NA, UNSR17$qn4a)
UNSR17$PREENG<- abs(UNSR17$qn4a-5)
UNSR17$PREENG<- factor(UNSR17$PREENG,levels = c(1,2,3,4), labels = c("Not at all", "Not Well", "Well", "Very Well"))
UNSR18$qn4a<- ifelse(UNSR18$qn4a== 8|UNSR18$qn4a==9, NA, UNSR18$qn4a)
UNSR18$PREENG<- abs(UNSR18$qn4a-5)
UNSR18$PREENG<- factor(UNSR18$PREENG,levels = c(1,2,3,4), labels = c("Not at all", "Not Well", "Well", "Very Well"))

UNSR19$qn4a<- ifelse(UNSR19$qn4a== 8|UNSR19$qn4a==9, NA, UNSR19$qn4a)
UNSR19$PREENG<- abs(UNSR19$qn4a-5)
Freq(UNSR19$PREENG)
UNSR19$PREENG<- factor(UNSR19$PREENG,levels = c(1,2,3,4), labels = c("Not at all", "Not Well", "Well", "Very Well"))


summary(UNSR16$PREENG)
Freq(UNSR17$PREENG)
Freq(UNSR18$PREENG)

```

## Region of Resettlement
```{r}
UNSR16$HOSTREG<-ifelse(UNSR16$qn1k==98| UNSR16$qn1k==99, NA, UNSR16$qn1k)

UNSR17$HOSTREG<-ifelse(UNSR17$qn1k==98| UNSR17$qn1k==99, NA, UNSR17$qn1k)

UNSR18$HOSTREG<-ifelse(UNSR18$qn1k==98| UNSR18$qn1k==99, NA, UNSR18$qn1k)
UNSR19$HOSTREG<-ifelse(UNSR19$qn1k==98| UNSR19$qn1k==99, NA, UNSR19$qn1k)

UNSR19$HOSTREG<- factor(UNSR19$HOSTREG,levels = c(1,2,3,4),labels = c("NorthEast", "South", "MidWest", "West"))

UNSR16$HOSTREG<- factor(UNSR16$HOSTREG,levels = c(1,2,3,4),labels = c("NorthEast", "South", "MidWest", "West"))

UNSR17$HOSTREG<- factor(UNSR17$HOSTREG,levels = c(1,2,3,4),labels = c("NorthEast", "South", "MidWest", "West"))

UNSR18$HOSTREG<- factor(UNSR18$HOSTREG,levels = c(1,2,3,4),labels = c("NorthEast", "South", "MidWest", "West"))

UNSR16$HOSTREG<-relevel(UNSR16$HOSTREG, ref = 4)
UNSR17$HOSTREG<-relevel(UNSR17$HOSTREG, ref = 4)
UNSR18$HOSTREG<-relevel(UNSR18$HOSTREG, ref = 4)
UNSR19$HOSTREG<-relevel(UNSR19$HOSTREG, ref = 4)                   

```

## Current Enrollement in Eng Program 1=No, 2=Yes
```{r}
UNSR16$CURENGEN<- ifelse(UNSR16$qn4e==8|UNSR16$qn4e==9, NA, ifelse(UNSR16$qn4e==6, 2, UNSR16$qn4e))

UNSR17$CURENGEN<- ifelse(UNSR17$qn4e==8|UNSR17$qn4e==9, NA, ifelse(UNSR17$qn4e==6, 2, UNSR17$qn4e))

UNSR18$CURENGEN<- ifelse(UNSR18$qn4e==8|UNSR18$qn4e==9, NA, ifelse(UNSR18$qn4e==6, 2, UNSR18$qn4e))


UNSR19$CURENGEN<- ifelse(UNSR19$qn4e==8|UNSR19$qn4e==9, NA, ifelse(UNSR19$qn4e==6, 2, UNSR19$qn4e))
#Factorize
UNSR16$CURENGEN<- factor(UNSR16$CURENGEN, levels = c(1,2), labels = c("No", "Yes"))

UNSR17$CURENGEN<- factor(UNSR17$CURENGEN, levels = c(1,2), labels = c("No", "Yes"))

UNSR18$CURENGEN<- factor(UNSR18$CURENGEN, levels = c(1,2), labels = c("No", "Yes"))
UNSR19$CURENGEN<- factor(UNSR19$CURENGEN, levels = c(1,2), labels = c("No", "Yes"))

```

## Current Enrollment in Employment Training Program
```{r}
UNSR16$CUREMPT<-ifelse(UNSR16$qn24a==8|UNSR16$qn24a==9, NA, UNSR16$qn24a)

UNSR17$CUREMPT<-ifelse(UNSR17$qn24a==8|UNSR17$qn24a==9, NA, UNSR17$qn24a)

UNSR18$CUREMPT<-ifelse(UNSR18$qn24a==8|UNSR18$qn24a==9, NA, UNSR18$qn24a)
UNSR19$CUREMPT<-ifelse(UNSR19$qn24a==8|UNSR19$qn24a==9, NA, UNSR19$qn24a)

#Factorizing

UNSR16$CUREMPT<- factor(UNSR16$CUREMPT, levels = c(1,2), labels = c("No", "Yes"))

UNSR17$CUREMPT<- factor(UNSR17$CUREMPT, levels = c(1,2), labels = c("No", "Yes"))

UNSR18$CUREMPT<- factor(UNSR18$CUREMPT, levels = c(1,2), labels = c("No", "Yes"))


UNSR19$CUREMPT<- factor(UNSR19$CUREMPT, levels = c(1,2), labels = c("No", "Yes"))
```

## English Proficiency Now Likert where 1=Very Well and 4=Not at all
```{r}
UNSR16$qn4b<- ifelse(UNSR16$qn4b==8|UNSR16$qn4b==9, NA, UNSR16$qn4b)
UNSR16$CURENG<- abs(UNSR16$qn4b-5)

UNSR17$qn4b<- ifelse(UNSR17$qn4b==8|UNSR17$qn4b==9, NA, UNSR17$qn4b)
UNSR17$CURENG<- abs(UNSR17$qn4b-5)

UNSR18$qn4b<- ifelse(UNSR18$qn4b==8|UNSR18$qn4b==9, NA, UNSR18$qn4b)
UNSR18$CURENG<- abs(UNSR18$qn4b-5)

UNSR19$qn4b<- ifelse(UNSR19$qn4b==8|UNSR19$qn4b==9, NA, UNSR19$qn4b)
UNSR19$CURENG<- abs(UNSR19$qn4b-5)

#Factorizing
UNSR16$CURENG<- factor(UNSR16$CURENG,levels = c(1,2,3,4), labels = c("Not at All", "Not Well", "Well", "Very Well"), ordered = F)

UNSR17$CURENG<- factor(UNSR17$CURENG,levels = c(1,2,3,4), labels = c("Not at All", "Not Well", "Well", "Very Well"), ordered = F)


UNSR18$CURENG<- factor(UNSR18$CURENG,levels = c(1,2,3,4), labels = c("Not at All", "Not Well", "Well", "Very Well"), ordered = F)

UNSR19$CURENG<- factor(UNSR19$CURENG,levels = c(1,2,3,4), labels = c("Not at All", "Not Well", "Well", "Very Well"), ordered = F)

Freq(UNSR16$CURENG)
Freq(UNSR17$CURENG)
Freq(UNSR18$CURENG)

```


## Sex 1=Male, 2=Female
```{r}
UNSR16$SEX<- ifelse(UNSR16$qn1f==8|UNSR16$qn1f==9, NA, UNSR16$qn1f)

UNSR17$SEX<- ifelse(UNSR17$qn1f==8|UNSR17$qn1f==9, NA, UNSR17$qn1f)

UNSR18$SEX<- ifelse(UNSR18$qn1f==8|UNSR18$qn1f==9, NA, UNSR18$qn1f)

UNSR19$SEX<- ifelse(UNSR19$qn1f==8|UNSR19$qn1f==9, NA, UNSR19$qn1f)

# Factorize
UNSR16$SEX<- factor(UNSR16$SEX, levels = c(1,2),labels = c("Male", "Female"))

UNSR17$SEX<- factor(UNSR17$SEX, levels = c(1,2),labels = c("Male", "Female"))


UNSR18$SEX<- factor(UNSR18$SEX, levels = c(1,2),labels = c("Male", "Female"))

UNSR19$SEX<- factor(UNSR19$SEX, levels = c(1,2),labels = c("Male", "Female"))

```

# Age 
```{r}
UNSR16$AGE<- ifelse(UNSR16$qn1d==999|UNSR16$qn1d==998, NA, UNSR16$qn1d)
UNASR16$KID<- ifelse(UNASR16$qn1d<16, 1, 0)

UNSR17$AGE<- ifelse(UNSR17$qn1d==999|UNSR17$qn1d==998, NA, UNSR17$qn1d)
UNASR17$KID<- ifelse(UNASR17$qn1d<16, 1, 0)

UNSR18$AGE<- ifelse(UNSR18$qn1d==999|UNSR18$qn1d==998, NA, UNSR18$qn1d)
UNASR18$KID<- ifelse(UNASR18$qn1d<16, 1, 0)

UNSR19$AGE<- ifelse(UNSR19$qn1d==999|UNSR19$qn1d==998, NA, UNSR19$qn1d)
UNASR19$KID<- ifelse(UNASR19$qn1d<16, 1, 0)
```

## How many people in the household
```{r}
summary(UNSR19$numppl)

```

## Marital Status 1=MArried, 2=Divorced/Seperated/widowed, 3=Never MArried, 4=Other, 5= R is a Child
```{r}

##2016
UNSR16$MARSTAT<-ifelse(UNSR16$qn1c== 8|UNSR16$qn1c== 9, NA, 
                       ifelse(UNSR16$qn1c== 2|UNSR16$qn1c== 3|UNSR16$qn1c== 5, 2, 
                              ifelse(UNSR16$qn1c== 4, 3,
                                     ifelse(UNSR16$qn1c== 7, 4,
                                            ifelse(UNSR16$qn1c== 6, 5, UNSR16$qn1c)))))
##2017
UNSR17$MARSTAT<-ifelse(UNSR17$qn1c== 8|UNSR17$qn1c== 9|UNSR17$qn1c== 0, NA, 
                       ifelse(UNSR17$qn1c== 2|UNSR17$qn1c== 3|UNSR17$qn1c== 5, 2, 
                              ifelse(UNSR17$qn1c== 4, 3,
                                     ifelse(UNSR17$qn1c== 7, 4,
                                            ifelse(UNSR17$qn1c== 6, 5, UNSR17$qn1c)))))
##2018
UNSR18$MARSTAT<-ifelse(UNSR18$qn1c== 8|UNSR18$qn1c== 9, NA, 
                       ifelse(UNSR18$qn1c== 2|UNSR18$qn1c== 3|UNSR18$qn1c== 5, 2, 
                              ifelse(UNSR18$qn1c== 4, 3,
                                     ifelse(UNSR18$qn1c== 7, 4,
                                            ifelse(UNSR18$qn1c== 6, 5, UNSR18$qn1c)))))

##2019
UNSR19$MARSTAT<-ifelse(UNSR19$qn1c== 8|UNSR19$qn1c== 9, NA, 
                       ifelse(UNSR19$qn1c== 2|UNSR19$qn1c== 3|UNSR19$qn1c== 5, 2, 
                              ifelse(UNSR19$qn1c== 4, 3,
                                     ifelse(UNSR19$qn1c== 7, 4,
                                            ifelse(UNSR19$qn1c== 6, 5, UNSR19$qn1c)))))


# FActorizing

UNSR16$MARSTAT<- factor(UNSR16$MARSTAT, levels = c(1,2,3,4,5), labels = c("Married", "Divorced/Seperated/Widowed", "Never Married", "Other", "R is a child"))

UNSR17$MARSTAT<- factor(UNSR17$MARSTAT, levels = c(1,2,3,4,5), labels = c("Married", "Divorced/Seperated/Widowed", "Never Married", "Other", "R is a child"))

UNSR18$MARSTAT<- factor(UNSR18$MARSTAT, levels = c(1,2,3,4,5), labels = c("Married", "Divorced/Seperated/Widowed", "Never Married", "Other", "R is a child"))

UNSR19$MARSTAT<- factor(UNSR19$MARSTAT, levels = c(1,2,3,4,5), labels = c("Married", "Divorced/Seperated/Widowed", "Never Married", "Other", "R is a child"))
```

## Presence of Dependents (People that have a condition or reason that limits the amount or kind of work they can do?) 1=no, 2=yes
```{r}

#Binaries for Individuals
UNASR16$DEPEND<- ifelse(UNASR16$qn28a== 8|UNASR16$qn28a== 9, NA, 
                       ifelse(UNASR16$qn28a== 1, 0, 
                              ifelse(UNASR16$qn28a== 2, 1, UNASR16$qn28a)))



#2017

UNASR17$DEPEND<- ifelse(UNASR17$qn28a== 8|UNASR17$qn28a== 9, NA, 
                       ifelse(UNASR17$qn28a== 1, 0, 
                              ifelse(UNASR17$qn28a== 2, 1, UNASR17$qn28a)))

#2018
UNASR18$DEPEND<- ifelse(UNASR18$qn28a== 8|UNASR18$qn28a== 9, NA, 
                       ifelse(UNASR18$qn28a== 1, 0, 
                              ifelse(UNASR18$qn28a== 2, 1, UNASR18$qn28a)))



#2019
UNASR19$DEPEND<- ifelse(UNASR19$qn28a== 8|UNASR19$qn28a== 9, NA, 
                       ifelse(UNASR19$qn28a== 1, 0, 
                              ifelse(UNASR19$qn28a== 2, 1, UNASR19$qn28a)))
# Add in the Kids to the Dependents KID is the var name
###2016
aK<-table(UNASR16$hhid, UNASR16$KID)
UNSR16$KIDS<- as.vector(aK[,2])
####2017
bK<-table(UNASR17$hhid, UNASR17$KID)
UNSR17$KIDS<- as.vector(bK[,2])
####2018
cK<-table(UNASR18$hhid, UNASR18$KID)
UNSR18$KIDS<- as.vector(cK[,2])
####2019
dK<-table(UNASR19$hhid, UNASR19$KID)
UNSR19$KIDS<- as.vector(dK[,2])




## Number of Dependents in household
###2016
a<-table(UNASR16$hhid, UNASR16$DEPEND)
UNSR16$DEPENDS<- as.vector(a[,2])
####2017
b<-table(UNASR17$hhid, UNASR17$DEPEND)
UNSR17$DEPENDS<- as.vector(b[,2])
####2018
c<-table(UNASR18$hhid, UNASR18$DEPEND)
UNSR18$DEPENDS<- as.vector(c[,2])
####2019
d<-table(UNASR19$hhid, UNASR19$DEPEND)
UNSR19$DEPENDS<- as.vector(d[,2])

##### Make the Household Level Dependents Dummy 
UNSR16<-UNSR16%>% mutate(DEPEND= case_when(DEPENDS>0~1,
                                           DEPENDS==0~0))
UNSR17<-UNSR17%>% mutate(DEPEND= case_when(DEPENDS>0~1,
                                           DEPENDS==0~0))
UNSR18<-UNSR18%>% mutate(DEPEND= case_when(DEPENDS>0~1,
                                           DEPENDS==0~0))
UNSR19<-UNSR19%>% mutate(DEPEND= case_when(DEPENDS>0~1,
                                           DEPENDS==0~0))

##Factorize
UNSR16$DEPEND<- factor(UNSR16$DEPEND, levels = c(0,1), labels = c("No Dependents", "Dependents"))

UNSR17$DEPEND<- factor(UNSR17$DEPEND, levels = c(0,1), labels = c("No Dependents", "Dependents"))

UNSR18$DEPEND<- factor(UNSR18$DEPEND, levels = c(0,1), labels = c("No Dependents", "Dependents"))

UNSR19$DEPEND<- factor(UNSR19$DEPEND, levels = c(0,1), labels = c("No Dependents", "Dependents"))
```

## Year of the Survey

```{r}
UNSR16$SVYYR<-2016
UNSR17$SVYYR<-2017
UNSR18$SVYYR<-2018
UNSR19$SVYYR<-2019


```

## MAKING DEPENDENCE ON PUBLIC ASSISTANCE PROGRAMS
```{r}
#Cleaning Food Stamps
UNSR16<-UNSR16%>% mutate(Foodstamps= case_when(qn30a==1~0,
                                               qn30a==2~1,
                                               qn30a==8~as.numeric(NA),
                                               qn30a==9~as.numeric(NA)))

UNSR17<-UNSR17%>% mutate(Foodstamps= case_when(qn30a==1~0,
                                               qn30a==2~1,
                                               qn30a==8~as.numeric(NA),
                                               qn30a==9~as.numeric(NA)))

UNSR18<-UNSR18%>% mutate(Foodstamps= case_when(qn30a==1~0,
                                               qn30a==2~1,
                                               qn30a==8~as.numeric(NA),
                                               qn30a==9~as.numeric(NA)))

UNSR19<-UNSR19%>% mutate(Foodstamps= case_when(qn30a==1~0,
                                               qn30a==2~1,
                                               qn30a==8~as.numeric(NA),
                                               qn30a==9~as.numeric(NA)))
#Factorizing
UNSR16$Foodstamps<-factor(UNSR16$Foodstamps,levels = c(0,1), labels = c(" Not On Foodstamps", "On foodstamps"))

UNSR17$Foodstamps<-factor(UNSR17$Foodstamps,levels = c(0,1), labels = c(" Not On Foodstamps", "On foodstamps"))

UNSR18$Foodstamps<-factor(UNSR18$Foodstamps,levels = c(0,1), labels = c(" Not On Foodstamps", "On foodstamps"), ordered = T)
UNSR19$Foodstamps<-factor(UNSR19$Foodstamps,levels = c(0,1), labels = c(" Not On Foodstamps", "On foodstamps"), ordered = T)
#Cleaning TANF
UNSR16<-UNSR16%>% mutate(TANF= case_when(qn31a==1~0,
                                               qn31a==2~1,
                                               qn31a==8~as.numeric(NA),
                                               qn31a==9~as.numeric(NA)))

UNSR17<-UNSR17%>% mutate(TANF= case_when(qn31a==1~0,
                                               qn31a==2~1,
                                               qn31a==8~as.numeric(NA),
                                               qn31a==9~as.numeric(NA)))

UNSR18<-UNSR18%>% mutate(TANF= case_when(qn31a==1~0,
                                               qn31a==2~1,
                                               qn31a==8~as.numeric(NA),
                                               qn31a==9~as.numeric(NA)))


UNSR19<-UNSR19%>% mutate(TANF= case_when(qn31a==1~0,
                                               qn31a==2~1,
                                               qn31a==8~as.numeric(NA),
                                               qn31a==9~as.numeric(NA)))

#Factorizing
UNSR16$TANF<-factor(UNSR16$TANF,levels = c(0,1), labels = c(" Not On TANF", "On TANF"))

UNSR17$TANF<-factor(UNSR17$TANF,levels = c(0,1), labels = c(" Not On TANF", "On TANF"))

UNSR18$TANF<-factor(UNSR18$TANF,levels = c(0,1), labels = c(" Not On TANF", "On TANF"))

UNSR19$TANF<-factor(UNSR19$TANF,levels = c(0,1), labels = c(" Not On TANF", "On TANF"))

#Cleaning RCA
UNSR16<-UNSR16%>% mutate(RCA= case_when(qn32a==1~0,
                                               qn32a==2~1,
                                               qn32a==8~as.numeric(NA),
                                               qn32a==9~as.numeric(NA)))

UNSR17<-UNSR17%>% mutate(RCA= case_when(qn32a==1~0,
                                               qn32a==2~1,
                                               qn32a==8~as.numeric(NA),
                                               qn32a==9~as.numeric(NA)))

UNSR18<-UNSR18%>% mutate(RCA= case_when(qn32a==1~0,
                                               qn32a==2~1,
                                               qn32a==8~as.numeric(NA),
                                               qn32a==9~as.numeric(NA)))

UNSR19<-UNSR19%>% mutate(RCA= case_when(qn32a==1~0,
                                               qn32a==2~1,
                                               qn32a==8~as.numeric(NA),
                                               qn32a==9~as.numeric(NA)))

#Factorizing
UNSR16$RCA<-factor(UNSR16$RCA,levels = c(0,1), labels = c(" Not On RCA", "On RCA"))

UNSR17$RCA<-factor(UNSR17$RCA,levels = c(0,1), labels = c(" Not On RCA", "On RCA"))

UNSR18$RCA<-factor(UNSR18$RCA,levels = c(0,1), labels = c(" Not On RCA", "On RCA"))

UNSR19$RCA<-factor(UNSR19$RCA,levels = c(0,1), labels = c(" Not On RCA", "On RCA"))

# Cleaning SSI
UNSR16<-UNSR16%>% mutate(SSI= case_when(qn33a==1~0,
                                               qn33a==2~1,
                                               qn33a==8~as.numeric(NA),
                                               qn33a==9~as.numeric(NA)))
UNSR17<-UNSR17%>% mutate(SSI= case_when(qn32a==1~0,
                                               qn33a==2~1,
                                               qn33a==8~as.numeric(NA),
                                               qn33a==9~as.numeric(NA)))
UNSR18<-UNSR18%>% mutate(SSI= case_when(qn32a==1~0,
                                               qn33a==2~1,
                                               qn33a==8~as.numeric(NA),
                                               qn33a==9~as.numeric(NA)))

UNSR19<-UNSR19%>% mutate(SSI= case_when(qn32a==1~0,
                                               qn33a==2~1,
                                               qn33a==8~as.numeric(NA),
                                               qn33a==9~as.numeric(NA)))


#Factorizing
UNSR16$SSI<-factor(UNSR16$SSI,levels = c(0,1), labels = c(" Not On SSI", "On SSI"))

UNSR17$SSI<-factor(UNSR17$SSI,levels = c(0,1), labels = c(" Not On SSI", "On SSI"))

UNSR18$SSI<-factor(UNSR18$SSI,levels = c(0,1), labels = c(" Not On SSI", "On SSI"))


UNSR19$SSI<-factor(UNSR19$SSI,levels = c(0,1), labels = c(" Not On SSI", "On SSI"))

#Cleaning General Assistance
UNSR16<-UNSR16%>% mutate(GA= case_when(qn34a==1~0,
                                               qn34a==2~1,
                                               qn34a==8~as.numeric(NA),
                                               qn34a==9~as.numeric(NA)))

UNSR17<-UNSR17%>% mutate(GA= case_when(qn34a==1~0,
                                               qn34a==2~1,
                                               qn34a==8~as.numeric(NA),
                                               qn34a==9~as.numeric(NA)))

UNSR18<-UNSR18%>% mutate(GA= case_when(qn34a==1~0,
                                               qn34a==2~1,
                                               qn34a==8~as.numeric(NA),
                                               qn34a==9~as.numeric(NA)))

UNSR19<-UNSR19%>% mutate(GA= case_when(qn34a==1~0,
                                               qn34a==2~1,
                                               qn34a==8~as.numeric(NA),
                                               qn34a==9~as.numeric(NA)))

#Factorizing
UNSR16$GA<-factor(UNSR16$GA,levels = c(0,1), labels = c(" Not On GA", "On GA"))

UNSR17$GA<-factor(UNSR17$GA,levels = c(0,1), labels = c(" Not On GA", "On GA"))

UNSR18$GA<-factor(UNSR18$GA,levels = c(0,1), labels = c(" Not On GA", "On GA"))

UNSR19$GA<-factor(UNSR19$GA,levels = c(0,1), labels = c(" Not On GA", "On GA"))


#Cleaning Religious/Sponsor/VolAgency/"Most Affected Area" cash assistance
UNSR16<-UNSR16%>% mutate(Miscash= case_when(qn35a==1~0,
                                               qn35a==2~1,
                                               qn35a==8~as.numeric(NA),
                                               qn35a==9~as.numeric(NA)))

UNSR17<-UNSR17%>% mutate(Miscash= case_when(qn35a==1~0,
                                               qn35a==2~1,
                                               qn35a==8~as.numeric(NA),
                                               qn35a==9~as.numeric(NA)))

UNSR18<-UNSR18%>% mutate(Miscash= case_when(qn35a==1~0,
                                               qn35a==2~1,
                                               qn35a==8~as.numeric(NA),
                                               qn35a==9~as.numeric(NA)))

UNSR19<-UNSR19%>% mutate(Miscash= case_when(qn35a==1~0,
                                               qn35a==2~1,
                                               qn35a==8~as.numeric(NA),
                                               qn35a==9~as.numeric(NA)))

#Factorizing
UNSR16$Miscash<-factor(UNSR16$Miscash,levels = c(0,1), labels = c(" Not On Miscash", "On Miscash"))

UNSR17$Miscash<-factor(UNSR17$Miscash,levels = c(0,1), labels = c(" Not On Miscash", "On Miscash"))

UNSR18$Miscash<-factor(UNSR18$Miscash,levels = c(0,1), labels = c(" Not On Miscash", "On Miscash"))

UNSR19$Miscash<-factor(UNSR19$Miscash,levels = c(0,1), labels = c(" Not On Miscash", "On Miscash"))
# Public Housing

UNSR16<-UNSR16%>% mutate(PubHo= case_when(qn38c==1~0,
                                               qn38c==2~1,
                                               qn38c==8~as.numeric(NA),
                                               qn38c==9~as.numeric(NA)))

UNSR17<-UNSR17%>% mutate(PubHo= case_when(qn38c==1~0,
                                               qn38c==2~1,
                                               qn38c==8~as.numeric(NA),
                                               qn38c==9~as.numeric(NA)))

UNSR18<-UNSR18%>% mutate(PubHo= case_when(qn38c==1~0,
                                               qn38c==2~1,
                                               qn38c==8~as.numeric(NA),
                                               qn38c==9~as.numeric(NA)))

UNSR19<-UNSR19%>% mutate(PubHo= case_when(qn38c==1~0,
                                               qn38c==2~1,
                                               qn38c==8~as.numeric(NA),
                                               qn38c==9~as.numeric(NA)))

#Factorizing
UNSR16$PubHo<-factor(UNSR16$PubHo,levels = c(0,1), labels = c(" Not On PubHo", "On PubHo"))

UNSR17$PubHo<-factor(UNSR17$PubHo,levels = c(0,1), labels = c(" Not On PubHo", "On PubHo"))

UNSR18$PubHo<-factor(UNSR18$PubHo,levels = c(0,1), labels = c(" Not On PubHo", "On PubHo"))

UNSR19$PubHo<-factor(UNSR19$PubHo,levels = c(0,1), labels = c(" Not On PubHo", "On PubHo"))
## Making The number of public assistance programs a household uses. 
UNSR16$NUM_PROGS <- (as.numeric(UNSR16$Foodstamps)-1)+(as.numeric(UNSR16$TANF)-1)+(as.numeric(UNSR16$RCA)-1)+(as.numeric(UNSR16$SSI)-1)+(as.numeric(UNSR16$GA)-1)+(as.numeric(UNSR16$Miscash)-1)+(as.numeric(UNSR16$PubHo)-1)

UNSR17$NUM_PROGS <- (as.numeric(UNSR17$Foodstamps)-1)+(as.numeric(UNSR17$TANF)-1)+(as.numeric(UNSR17$RCA)-1)+(as.numeric(UNSR17$SSI)-1)+(as.numeric(UNSR17$GA)-1)+(as.numeric(UNSR17$Miscash)-1)+(as.numeric(UNSR17$PubHo)-1)

UNSR18$NUM_PROGS <- as.numeric(UNSR18$Foodstamps)+as.numeric(UNSR18$TANF)+as.numeric(UNSR18$RCA)+as.numeric(UNSR18$SSI)+as.numeric(UNSR18$GA)+as.numeric(UNSR18$Miscash)+as.numeric(UNSR18$PubHo)-7

UNSR19$NUM_PROGS <- as.numeric(UNSR19$Foodstamps)+as.numeric(UNSR19$TANF)+as.numeric(UNSR19$RCA)+as.numeric(UNSR19$SSI)+as.numeric(UNSR19$GA)+as.numeric(UNSR19$Miscash)+as.numeric(UNSR19$PubHo)-7

```

## Make dicotomous Financial Independence   
```{r}

UNSR16<-UNSR16 %>% mutate(FD=case_when(NUM_PROGS==0~0,
                               NUM_PROGS>0~1))

UNSR17<-UNSR17 %>% mutate(FD=case_when(NUM_PROGS==0~0,
                               NUM_PROGS>0~1))

UNSR18<-UNSR18 %>% mutate(FD=case_when(NUM_PROGS==0~0,
                               NUM_PROGS>0~1))

UNSR19<-UNSR19 %>% mutate(FD=case_when(NUM_PROGS==0~0,
                               NUM_PROGS>0~1))

```

## Peeling off unused variables
```{r}




which(colnames(UNSR19)== "WHENJOB")
which(colnames(UNSR19)== "NUM_PROGS")
which(colnames(UNSR19)== "Weight_household")

#include 181:220 for the household weights
temp16<- UNSR16[,c(1,3,179,333:361)]
which(colnames(UNSR16)== "WHENJOB")
which(colnames(UNSR16)== "NUM_PROGS")

#@include 140:159 for the household replicant weights
temp17<- UNSR17[,c(1,3,138,253:281)]
which(colnames(UNSR17)== "WHENJOB")
which(colnames(UNSR17)== "NUM_PROGS")

#include 154:180 for the household replicant weights. 
temp18<- UNSR18[,c(1,3,152,281:309)]
temp19<- UNSR19[,c(1,6,146,265:293)]
```

## Imputating missing data



```{r, echo=FALSE, }

imp16<- mice(temp16, predictorMatrix = quickpred(temp16, exclude= c("hhid", "Weight_household","ORIGIN","MARSTAT", "Foodstamps", "TANF", "RCA", "GA","Miscash", "PubHo", "NUM_PROGS")),m = 21)
imp17<- mice(temp17, predictorMatrix = quickpred(temp17, exclude= c("hhid", "Weight_household", "ORIGIN","MARSTAT", "Foodstamps", "TANF", "RCA", "GA","Miscash", "PubHo", "NUM_PROGS")),m = 21)

imp18<- mice(temp18, predictorMatrix = quickpred(temp18, exclude= c("hhid","ECOSECTOR", "Weight_household","ORIGIN","MARSTAT", "Foodstamps", "TANF", "RCA", "GA","Miscash", "PubHo", "NUM_PROGS")),m = 21)

imp19<- mice(temp19, predictorMatrix = quickpred(temp19, exclude= c("hhid","ECOSECTOR", "Weight_household","ORIGIN","MARSTAT", "Foodstamps", "TANF", "RCA", "GA","Miscash", "PubHo", "NUM_PROGS")),m = 21)
```

```{r}

#Time Till First job in the United States
imp16$data$TILLJOBb<- imp16$data$WHENJOB-imp16$data$WHENARRIVE
imp17$data$TILLJOBb<- imp17$data$WHENJOB-imp17$data$WHENARRIVE
imp18$data$TILLJOBb<- imp18$data$WHENJOB-imp18$data$WHENARRIVE
imp19$data$TILLJOBb<- imp19$data$WHENJOB-imp19$data$WHENARRIVE
table(imp16$data$TILLJOBb)

#Handles the negative values to their proper positions, I assume those who say obtain jobs before they arrive obtain jobs the same year they arrive. n=30. 
imp16$data<- imp16$data%>%mutate(TILLJOBb= case_when(TILLJOBb<0 & TILLJOBb>-6~0,
                                                     TILLJOBb<=-100~6,
                                                    .default= TILLJOBb))
imp17$data<- imp17$data%>%mutate(TILLJOBb= case_when(TILLJOBb<=-100~6,
                                                    TILLJOBb<0 & TILLJOBb>-6~0,
                                                    .default= TILLJOBb))
imp18$data<- imp18$data%>%mutate(TILLJOBb= case_when(TILLJOBb<=-100~6,
                                                    TILLJOBb<0 & TILLJOBb>-6~0,
                                                    .default= TILLJOBb))
imp19$data<- imp19$data%>%mutate(TILLJOBb= case_when(TILLJOBb<=-100~6,
                                                    TILLJOBb<0 & TILLJOBb>-6~0,
                                                    .default= TILLJOBb))
table(imp16$data$TILLJOBb)

#This makes a time to job dummy. This uses the imputed values so everyone has a assignment as either no job or our best estimate on obtaining a job. 
imp16$data<- imp16$data%>%mutate(TILLJOB= case_when(TILLJOBb==0~1,
                                                    TRUE~0))
imp17$data<- imp17$data%>%mutate(TILLJOB= case_when(TILLJOBb==0~1,
                                                    TRUE~0))
imp18$data<- imp18$data%>%mutate(TILLJOB= case_when(TILLJOBb==0~1,
                                                    TRUE~0))
imp19$data<- imp19$data%>%mutate(TILLJOB= case_when(TILLJOBb==0~1,
                                                    TRUE~0))
table(imp16$data$TILLJOB)

imp16$data$TILLJOBc<-factor(imp16$data$TILLJOBb, labels = c("Same Year", "1 year", "2 years", "3 years", "4 years", "Never"))
imp17$data$TILLJOBc<-factor(imp17$data$TILLJOBb, labels = c("Same Year", "1 year", "2 years", "3 years", "4 years","5 years", "Never"))
imp18$data$TILLJOBc<-factor(imp18$data$TILLJOBb, labels = c("Same Year", "1 year", "2 years", "3 years", "4 years","5 years", "Never"))
imp19$data$TILLJOBc<-factor(imp19$data$TILLJOBb, labels = c("Same Year", "1 year", "2 years", "3 years", "4 years", "Never"))
table(imp17$data$TILLJOBb)

imp16$data$TILLJOBb<- ifelse(imp16$data$TILLJOBb==6, NA, imp16$data$TILLJOBb)
imp17$data$TILLJOBb<- ifelse(imp17$data$TILLJOBb==6, NA, imp17$data$TILLJOBb)
imp18$data$TILLJOBb<- ifelse(imp18$data$TILLJOBb==6, NA, imp18$data$TILLJOBb)
imp19$data$TILLJOBb<- ifelse(imp19$data$TILLJOBb==6, NA, imp19$data$TILLJOBb)
table(as.numeric(imp16$data$TILLJOBb))
```
```{r}

temp16$TILLJOB<- imp16$data$TILLJOB
temp16$TILLJOBb<-imp16$data$TILLJOBb
temp16$TILLJOBc<-imp16$data$TILLJOBc

temp17$TILLJOB<- imp17$data$TILLJOB
temp17$TILLJOBb<-imp17$data$TILLJOBb
temp17$TILLJOBc<-imp17$data$TILLJOBc

temp18$TILLJOB<- imp18$data$TILLJOB
temp18$TILLJOBb<-imp18$data$TILLJOBb
temp18$TILLJOBc<-imp18$data$TILLJOBc

temp19$TILLJOB<- imp19$data$TILLJOB
temp19$TILLJOBb<-imp19$data$TILLJOBb
temp19$TILLJOBc<-imp19$data$TILLJOBc


```

#### making the pooled and weighted dataset
```{r}

#Making the TILL jobs variables in each TEMP

temp16$TILLJOBb<-imp16$data$TILLJOBb 
temp17$TILLJOBb<-imp17$data$TILLJOBb 
temp18$TILLJOBb<-imp18$data$TILLJOBb 
temp19$TILLJOBb<-imp19$data$TILLJOBb

temp16$TILLJOB<-imp16$data$TILLJOB
temp17$TILLJOB<-imp17$data$TILLJOB
temp18$TILLJOB<-imp18$data$TILLJOB
temp19$TILLJOB<-imp19$data$TILLJOB
#Generating Weights
wtemp16<- svydesign(ids=~hhid, weights =~Weight_household,data = temp16 )
wtemp17<- svydesign(ids=~hhid, weights =~Weight_household,data = temp17 )
wtemp18<- svydesign(ids=~hhid, weights =~Weight_household,data = temp18 )
wtemp19<- svydesign(ids=~hhid, weights =~Weight_household,data = temp19 )

compare_df_cols(temp16, temp17, temp18, temp19)
POOLED<- base::rbind(temp16,temp17, temp18, temp19) 

wPOOLED<- svydesign(ids=~hhid, weights =~Weight_household,data = POOLED )
```

```{r, echo=FALSE}
impPOOLED<- mice(POOLED, predictorMatrix = quickpred(POOLED, exclude= c("hhid", "Weight_household","ORIGIN","MARSTAT", "Foodstamps", "TANF", "RCA", "GA","Miscash", "PubHo", "NUM_PROGS", "TILLJOB", "TILLJOBb")),m = 21)

```


## assessing imputed dataframes 
```{r}
imp16$method
```

# Descriptive Statistics
## Pre-Migration Economic Sector
```{r error=TRUE}
library(DescTools)
Desc(temp16$ECOSECTOR)
Desc(temp17$ECOSECTOR)
Desc(temp18$ECOSECTOR)
Desc(POOLED$ECOSECTOR)
```


## Working Hours


```{r}
summary(temp16$WEEKHOUR)
summary(temp17$WEEKHOUR)
summary(temp18$WEEKHOUR)
```
##Region of Resettlment

```{r error=TRUE}
Desc(temp16$HOSTREG)

Desc(temp17$HOSTREG)

Desc(temp18$HOSTREG)

Desc(POOLED$HOSTREG)

```

## National Origin
```{r}

Freq(temp16$ORIGIN)
Freq(temp17$ORIGIN)
Freq(temp18$ORIGIN)
Freq(POOLED$ORIGIN)
```

## Current Enrollement in English Training Programs

```{R}
Freq(temp16$CURENGEN)

Freq(temp17$CURENGEN)

Freq(temp18$CURENGEN)

Freq(POOLED$CURENGEN)

```

## Current Enrollement in Employment training programs


```{r}
Freq(temp16$CUREMPT)
Freq(temp17$CUREMPT)
Freq(temp18$CUREMPT)
Freq(POOLED$CUREMPT)

```

## Current English Proficiency

```{r}
Freq(temp16$CURENG)
Freq(temp17$CURENG)
Freq(temp18$CURENG)
Freq(POOLED$CURENG)
sd(as.numeric(POOLED$CURENG), na.rm=T)
```

## Sex

```{r}

Freq(temp16$SEX)
Freq(temp17$SEX)
Freq(temp18$SEX)
Freq(POOLED$SEX)
```

## Marital Status

```{r}
Freq(temp16$MARSTAT)

Freq(temp17$MARSTAT)

Freq(temp18$MARSTAT)

Freq(POOLED$MARSTAT)
```

## Number of Dependents in household

```{r}
summary(temp16$DEPENDS)
sd(temp16$DEPENDS)
summary(temp17$DEPENDS)
sd(temp17$DEPENDS)
summary(temp18$DEPENDS)
sd(temp18$DEPENDS)
summary(POOLED$DEPENDS)
sd(POOLED$DEPENDS)

```

## Years of Education

```{r}
summary(temp16$EDUC)
sd(temp16$EDUC, na.rm=T)
```
## Context Variable   
```{r}
summary(temp16$CONTEXT)
sd(temp16$CONTEXT, na.rm= T)

summary(temp17$CONTEXT)
sd(temp17$CONTEXT, na.rm= T)

summary(temp18$CONTEXT)
sd(temp18$CONTEXT, na.rm= T)

summary(POOLED$CONTEXT)
sd(POOLED$CONTEXT, na.rm= T)
```

## PreMigration English Proficiency


```{r}

summary(temp16$PREENG)
summary(temp16$CURENG)
```

# Analysis with the imputed models

##First FI Pooled "Basics" Nest
```{r}
basicsPOOLED<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS, family = "binomial",design = wPOOLED))
BPoolpool<-pool(basicsPOOLED)
summary(BPoolpool)
```




## Second Pre Context Nest
```{r}
pcpool<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,ref="Iraq")+relevel(ECOSECTOR, "Other"), family = "binomial",design =wPOOLED ))
preconPOOLED<- pool(pcpool)
summary(preconPOOLED)
```


## Third Post Context Nest
```{r}
pocopool<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,ref="Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR, family = "binomial", design = wPOOLED))
posconPOOLED<- pool(pocopool)
summary(posconPOOLED)
```


## Fourth, Add Pre-Human Capital Vars
```{r}

prehupool<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,ref="Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+EDUC+CONTEXT+PREENG , family = "binomial", design = wPOOLED))
prehuPOOLED<- pool(prehupool)
summary(prehuPOOLED)
```


#Fith, the Final Model (Use this model for intra-model prediction comparisons)
```{r}

pohupool<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,ref="Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+EDUC+CONTEXT+PREENG+CURENGEN+CUREMPT+CURENG+relevel(URECOSEC, ref=2)+TILLJOBb+WEEKHOUR , family = "binomial", design =  wPOOLED ))
posthuPOOLED<- pool(pohupool)
a<-summary(posthuPOOLED)
```
## Comparing Results with unimputed data
```{r}
unweighted_POOLED_ES<-svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN, ref="Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+EDUC+PREENG+CURENGEN+CUREMPT+CURENG+relevel(URECOSEC, ref=2)+TILLJOBb+WEEKHOUR , family = "binomial", design = wPOOLED)

unweighted_POOLED_ES$aic
```
## What about factorizing survey year?
```{r}

pohupool<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+relevel(factor(SVYYR), ref = "2016")+EDUC+PREENG+CURENGEN+CUREMPT+CURENG+relevel(URECOSEC, ref=2)+TILLJOB+WEEKHOUR , family = "binomial", design = wPOOLED))
posthuPOOLED<- pool(pohupool)
summary(posthuPOOLED)
```


##Making the prediction dataframe.
### AIC AND BIC

```{r}
#comparing AIC's in both models I already have the context +Basics model
posconPOOLED$glanced
POOLED$URECOSEC<-relevel(POOLED$URECOSEC, ref=2)
#making the basics+human capital model
compareFIpool<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+EDUC+PREENG+CURENGEN+CUREMPT+CURENG+URECOSEC+TILLJOBb , family = "binomial", design = wPOOLED))
compareFIHCPOOLED<- pool(compareFIpool)
compareFIHCPOOLED$glanced
#The human capital one has the lower AIC and BIC
```

### Non-Miced predictions
```{r}

POOLED$URECOSEC<-relevel(POOLED$URECOSEC, ref=2)
modela <- svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+EDUC+PREENG+CURENGEN+CUREMPT+CURENG+relevel(URECOSEC, ref=2)+TILLJOB+WEEKHOUR , family = "binomial", design = wPOOLED)

summary(modela)
#Making the hypothetical dataframe for a maximally advantaged contextual person. 
maxconpred <- data.frame(RESIDENCY=factor(3), SEX="Male", AGE=39.7, numppl=3, MARSTAT="Never Married", TILLJOB=1, EDUC=12, ECOSECTOR="Professional", URECOSEC="Retail/Sales", ORIGIN="Cuba", PREENG="Not Well", HOSTREG="South", CURENGEN="No", CUREMPT="No", CURENG="Well", DEPENDS=1, SVYYR=2018, WEEKHOUR=38.33, TILLJOBb=1)


maxhumpred <- data.frame(RESIDENCY=factor(3), SEX="Male", AGE=39.7, numppl=3, MARSTAT="Never Married", TILLJOB=1, EDUC=20, ECOSECTOR="Other", URECOSEC= "Professional/ED/Health/SocialServices", ORIGIN="Iraq", PREENG="Very Well", HOSTREG="West", CURENGEN="No", CUREMPT="No", CURENG="Very Well", DEPENDS=1, SVYYR=2016, WEEKHOUR=38.33, TILLJOBb=1)
#NEED to Add KIDS to make predictions
#predict(modela, newdata =maxconpred, type = "response")

#predict(modela, newdata =maxhumpred, type = "response")
```


#2016 Fith, the Final Model (Use this model for intra-model prediction comparisons)
```{r}

pohu19<- with(imp19, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+HOSTREG+EDUC+CONTEXT+PREENG+ CURENGEN+CUREMPT+CURENG+relevel(URECOSEC, ref=2)+ TILLJOBb+WEEKHOUR , family = "binomial", design = wtemp19))
posthu19<- pool(pohu19)
summary(posthu19)
```

# 2017 FI Models 
## Basicis Model
```{r}
basics17<- with(imp17, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS, family = "binomial",design = wtemp17))
B17pool<-pool(basics17)
summary(B17pool)


```

## Second Pre Context Nest
```{r}
pc17<- with(imp17, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other"), family = "binomial",design =wtemp17 ))
precon17<- pool(pc17)
summary(precon17)
```

## Third Post Context Nest
```{r}
poco17<- with(imp17, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR, family = "binomial", design = wtemp17))
poscon17<- pool(poco17)
summary(poscon17)
```

## Fourth, Add Pre-Human Capital Vars
```{r}

prehu17<- with(imp17, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+EDUC+CONTEXT+PREENG , family = "binomial", design = wtemp17))
prehu17<- pool(prehu17)
summary(prehu17)

```

#Fith, the Final Model (Use this model for intra-model prediction comparisons)
```{r}

pohu17<- with(imp17, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+HOSTREG+relevel(URECOSEC, ref=2)+EDUC+CONTEXT+relevel(ECOSECTOR, "Other")+PREENG+ CURENGEN+CUREMPT+CURENG+ TILLJOBb+WEEKHOUR , family = "binomial", design = wtemp17))
posthu17<- pool(pohu17)
summary(posthu17)
```

# 2018 FI Models 
## Basicis Model
```{r}
basics18<- with(imp18, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS, family = "binomial",design = wtemp18))
B18pool<-pool(basics18)
summary(B18pool)


```

## Second Pre Context Nest
```{r}
pc18<- with(imp18, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other"), family = "binomial",design =wtemp18 ))
precon18<- pool(pc18)
summary(precon18)
```

## Third Post Context Nest
```{r}
poco18<- with(imp18, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR, family = "binomial", design = wtemp18))
poscon18<- pool(poco18)
summary(poscon18)
```

## Fourth, Add Pre-Human Capital Vars
```{r}

prehu18<- with(imp18, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+EDUC+CONTEXT+PREENG , family = "binomial", design = wtemp18))
prehu18<- pool(prehu18)
summary(prehu18)

```

#Fith, the Final Model (Use this model for intra-model prediction comparisons)
```{r}

pohu18<- with(imp18, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+HOSTREG+relevel(URECOSEC, ref=2)+EDUC+CONTEXT+relevel(ECOSECTOR, "Other")+PREENG+ CURENGEN+CUREMPT+CURENG+ TILLJOBb+WEEKHOUR , family = "binomial", design = wtemp18))
posthu18<- pool(pohu18)
summary(posthu18)
```

#  TIme to First Job 

## First Pooled "Basics" Nest
```{r}
basicsTJPOOLED<- with(impPOOLED, svyglm(TILLJOB~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS, family = "binomial",design = wPOOLED))
BPoolTJpool<-pool(basicsTJPOOLED)
summary(BPoolTJpool)
```


## Second Pre Context Nest
```{r}
pcTJpool<- with(impPOOLED,svyglm(TILLJOB~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+relevel(ORIGIN,"Iraq" )+relevel(ECOSECTOR,"Other"), family = "binomial",design =wPOOLED ))
preconTJPOOLED<- pool(pcTJpool)
summary(preconTJPOOLED)
```


## Third Post Context Nest
```{r}
pocoTJpool<- with(impPOOLED, svyglm(TILLJOB~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+relevel(ORIGIN,"Iraq")+relevel(ECOSECTOR,ref = "Other")+HOSTREG+SVYYR, family = "binomial", design = wPOOLED))
posconTJPOOLED<- pool(pocoTJpool)
summary(posconTJPOOLED)
```


## Fourth, Add Pre-Human Capital Vars (Final? because Till job may be before current variables)
```{r}
prezhuTJpool<- with(impPOOLED, svyglm(TILLJOB~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+relevel(ORIGIN,"Iraq")+relevel(ECOSECTOR,"Other")+HOSTREG+SVYYR+EDUC+PREENG, family = "binomial", design = wPOOLED))
prezhuTJPOOLED<- pool(prezhuTJpool)
summary(prezhuTJPOOLED)

```

## Firth, the final model
```{r}

prehuTJpool<- with(impPOOLED, svyglm(TILLJOB~ as.numeric(RESIDENCY)+ SEX+AGE+numppl+MARSTAT+DEPENDS+relevel(ORIGIN,"Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+EDUC+CONTEXT+EDUC+PREENG+CURENGEN:PREENG+CUREMPT+CURENG, family = "binomial", design = wPOOLED))
prehuTJPOOLED<- pool(prehuTJpool)
summary(prehuTJPOOLED)
```

```{r}
#Supplemantal Models
TJ_pooled_unmiced<-svyglm(TILLJOB~ as.numeric(RESIDENCY)+ SEX+AGE+numppl+MARSTAT+DEPENDS+relevel(ORIGIN,"Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+EDUC+CONTEXT+EDUC+PREENG+CURENGEN+CUREMPT+CURENG, family = "binomial", design = wPOOLED)
summary(TJ_pooled_unmiced)
TJ_pooled_unmiced
#2016
summary(svyglm(TILLJOB~ as.numeric(RESIDENCY)+ SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,"Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+EDUC+CONTEXT+EDUC+PREENG+CURENGEN+CUREMPT+CURENG, family = "binomial", design = wtemp16))

#2017
summary(svyglm(TILLJOB~ as.numeric(RESIDENCY)+ SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,"Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+EDUC+CONTEXT+EDUC+PREENG+CURENGEN+CUREMPT+CURENG, family = "binomial", design = wtemp17))

#2018 #have to take out Pre=EcoSector because no variation. This is also true for the 2019 model. 
summary(svyglm(TILLJOB~ as.numeric(RESIDENCY)+ SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,"Iraq")++HOSTREG+EDUC+CONTEXT+EDUC+PREENG+CURENGEN+CUREMPT+CURENG, family = "binomial", design = wtemp18))


#2019
summary(svyglm(TILLJOB~ as.numeric(RESIDENCY)+ SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,"Iraq")+HOSTREG+EDUC+CONTEXT+EDUC+PREENG+CURENGEN+CUREMPT+CURENG, family = "binomial", design = wtemp19))
```

# The comparisons between contexts and human capital
```{r}
posconTJPOOLED$glanced

compareTJpool<- with(impPOOLED, svyglm(TILLJOB~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+EDUC+PREENG+CURENGEN+CUREMPT+CURENG+URECOSEC , family = "binomial", design = wPOOLED))
compareTJHCPOOLED<- pool(compareTJpool)
compareTJHCPOOLED$glanced
## Contexts are better at the AIC and BIC measures, but what about Predicted probabilities?
```
### PRedicted Probabilities
```{r}
modelb <- svyglm(TILLJOB~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+EDUC+PREENG+CURENGEN+CUREMPT+CURENG+URECOSEC+TILLJOBb , family = "binomial", design = wPOOLED)


#Making the hypothetical dataframe for a maximally advantaged contextual person. 
maxconpred <- data.frame(RESIDENCY=factor(3), SEX="Male", AGE=39.7, numppl=3, MARSTAT="Never Married", TILLJOB=1, EDUC=12, ECOSECTOR="Professional", URECOSEC="Retail/Sales", ORIGIN="Cuba", PREENG="Not Well", HOSTREG="South", CURENGEN="No", CUREMPT="No", CURENG="Well", DEPENDS=1, KIDS=1, SVYYR=2018, WEEKHOUR=38.33, TILLJOBb=1)


maxhumpred <- data.frame(RESIDENCY=factor(3), SEX="Male", AGE=39.7, numppl=3, MARSTAT="Never Married", TILLJOB=1, EDUC=20, ECOSECTOR="Other", URECOSEC= "Professional/ED/Health/SocialServices", ORIGIN="Iraq", PREENG="Very Well", HOSTREG="West", CURENGEN="No", CUREMPT="No", CURENG="Very Well", DEPENDS=1, KIDS=1, SVYYR=2016, WEEKHOUR=38.33, TILLJOBb=1)

predict(modelb, newdata =maxconpred, type = "response")

predict(modelb, newdata =maxhumpred, type = "response")
```
# Log of Weekly Working Hours

##First FI Pooled "Basics" Nest
```{r}
WHbasicsPOOLED<- with(impPOOLED, svyglm(log(WEEKHOUR +1089/40) ~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS,design = wPOOLED))
WHBPoolpool<-pool(WHbasicsPOOLED)
summary(WHBPoolpool)
```




## Second Pre Context Nest
```{r}
WHpcpool<- with(impPOOLED, svyglm(log(WEEKHOUR +1089/40)~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other"),design =wPOOLED ))
WHpreconPOOLED<- pool(WHpcpool)
summary(WHpreconPOOLED)
```


## Third Post Context Nest
```{r}
WHpocopool<- with(impPOOLED, svyglm(log(WEEKHOUR +1089/40)~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR, design = wPOOLED))
WHposconPOOLED<- pool(WHpocopool)
summary(WHposconPOOLED)
```


## Fourth, Add Pre-Human Capital Vars
```{r}

WHprehupool<- with(impPOOLED, svyglm(log(WEEKHOUR +1089/40)~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+EDUC+CONTEXT+PREENG, design = wPOOLED))
WHprehuPOOLED<- pool(WHprehupool)
summary(WHprehuPOOLED)

```



#Fith, the Final Model (Use this model for intra-model prediction comparisons)
```{r}

WHpohupool<- with(impPOOLED, svyglm(log(WEEKHOUR +1089/40)~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+EDUC+CONTEXT+PREENG+CURENGEN+CUREMPT+CURENG+relevel(URECOSEC, ref=2)+TILLJOB+FI, design = wPOOLED))
WHposthuPOOLED<- pool(WHpohupool)
summary(WHposthuPOOLED)

```


# Comparing weekly working hours across maximal individuals

```{r}
WHposconPOOLED$glanced

compareWHpool<- with(impPOOLED, svyglm(log(WEEKHOUR +1089/40)~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+EDUC+PREENG+CURENGEN+CUREMPT+CURENG+URECOSEC+TILLJOBb, design = wPOOLED))
compareWHHCPOOLED<- pool(compareWHpool)
compareWHHCPOOLED$glanced
## Contexts are better at the AIC and BIC measures, but what about Predicted probabilities?

```



```{r}
modelc <- svyglm(log(WEEKHOUR +1089/40)~ as.numeric(RESIDENCY)+SEX+AGE+numppl+MARSTAT+DEPENDS+KIDS+EDUC+PREENG+CURENGEN+CUREMPT+CURENG+URECOSEC+TILLJOBb, design = wPOOLED)


#Making the hypothetical dataframe for a maximally advantaged contextual person. 
maxconpred <- data.frame(RESIDENCY=factor(3), SEX="Male", AGE=39.7, numppl=3, MARSTAT="Never Married", KIDS=1, TILLJOB=1, EDUC=12, ECOSECTOR="Professional", URECOSEC="Retail/Sales", ORIGIN="Cuba", PREENG="Not Well", HOSTREG="South", CURENGEN="No", CUREMPT="No", CURENG="Well", DEPENDS=1, SVYYR=2018, WEEKHOUR=38.33, TILLJOBb=1)


maxhumpred <- data.frame(RESIDENCY=factor(3), SEX="Male", AGE=39.7, numppl=3, MARSTAT="Never Married", KIDS=1, TILLJOB=1, EDUC=20, ECOSECTOR="Other", URECOSEC= "Professional/ED/Health/SocialServices", ORIGIN="Iraq", PREENG="Very Well", HOSTREG="West", CURENGEN="No", CUREMPT="No", CURENG="Very Well", DEPENDS=1, SVYYR=2016, WEEKHOUR=38.33, TILLJOBb=1)

predict(modelc, newdata =maxconpred, type = "response")

predict(modelc, newdata =maxhumpred, type = "response")

```

# The Group-by Descriptive I need

```{r}
result <- UNSR17 %>%
  group_by(RESIDENCY, ui_soi_pubassist) %>%
  summarise(count = n()) %>%
  mutate(percent = count / sum(count) * 100)
print(result)
```
# For Canadian Comparisons
I need to find the proportion of economically self-sufficient refugees in each American cohort. They need to be weighted. 

```{r}
USin19cohort14<- UNSR19[UNSR19$RESIDENCY==2014,]
USin19cohort14<- USin19cohort14[!(is.na(USin19cohort14$hhid)),]
USin19cohort14_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin19cohort14,na.rm=T)
svymean(USin19cohort14$FI, USin19cohort14_w, na.rm=T)
```
Now for USin19cohort15
```{r}
USin19cohort15<- UNSR19[UNSR19$RESIDENCY==2015,]
USin19cohort15<- USin19cohort15[!(is.na(USin19cohort15$hhid)),]
USin19cohort15_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin19cohort15,na.rm=T)
USin19cohort15$FI
```
```{r}
USin19cohort16<- UNSR19[UNSR19$RESIDENCY==2016,]
USin19cohort16<- USin19cohort16[!(is.na(USin19cohort16$hhid)),]
USin19cohort16_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin19cohort16,na.rm=T)
USin19cohort16$FI
```
```{r}
USin19cohort17<- UNSR19[UNSR19$RESIDENCY==2017,]
USin19cohort17<- USin19cohort17[!(is.na(USin19cohort17$hhid)),]
USin19cohort17_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin19cohort17,na.rm=T)
USin19cohort17$FI
```
```{r}
USin19cohort18<- UNSR19[UNSR19$RESIDENCY==2018,]
USin19cohort18<- USin19cohort18[!(is.na(USin19cohort18$hhid)),]
USin19cohort18_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin19cohort18,na.rm=T)
USin19cohort18$FI
```
Now for the 2018.
```{r}
USin18cohort17<- UNSR18[UNSR18$RESIDENCY==2017,]
USin18cohort17<- USin18cohort17[!(is.na(USin18cohort17$hhid)),]
USin18cohort17_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin18cohort17,na.rm=T)
USin18cohort17$FI
```
```{r}
USin18cohort16<- UNSR18[UNSR18$RESIDENCY==2016,]
USin18cohort16<- USin18cohort16[!(is.na(USin18cohort16$hhid)),]
USin18cohort16_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin18cohort16,na.rm=T)
USin18cohort16$FI
```
```{r}
USin18cohort15<- UNSR18[UNSR18$RESIDENCY==2015,]
USin18cohort15<- USin18cohort15[!(is.na(USin18cohort15$hhid)),]
USin18cohort15_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin18cohort15,na.rm=T)
USin18cohort15$FI
```
```{r}
USin18cohort14<- UNSR18[UNSR18$RESIDENCY==2014,]
USin18cohort14<- USin18cohort14[!(is.na(USin18cohort14$hhid)),]
USin18cohort14_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin18cohort14,na.rm=T)
USin18cohort14$FI
```
```{r}
USin18cohort13<- UNSR18[UNSR18$RESIDENCY==2013,]
USin18cohort13<- USin18cohort13[!(is.na(USin18cohort13$hhid)),]
USin18cohort13_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin18cohort13,na.rm=T)
USin18cohort13$FI
```
Now for 2017

```{r}
USin17cohort16<- UNSR17[UNSR17$RESIDENCY==2016,]
USin17cohort16<- USin17cohort16[!(is.na(USin17cohort16$hhid)),]
USin17cohort16_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin17cohort16,na.rm=T)
svymean(USin17cohort16$FI, USin17cohort16_w, na.rm=T)
```
```{r}
USin17cohort15<- UNSR17[UNSR17$RESIDENCY==2015,]
USin17cohort15<- USin17cohort15[!(is.na(USin17cohort15$hhid)),]
USin17cohort15_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin17cohort15,na.rm=T)
svymean(USin17cohort15$FI, USin17cohort15_w, na.rm=T)
```

```{r}
USin17cohort14<- UNSR17[UNSR17$RESIDENCY==2014,]
USin17cohort14<- USin17cohort14[!(is.na(USin17cohort14$hhid)),]
USin17cohort14_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin17cohort14,na.rm=T)
svymean(USin17cohort14$FI, USin17cohort14_w, na.rm=T)
```

```{r}
USin17cohort13<- UNSR17[UNSR17$RESIDENCY==2013,]
USin17cohort13<- USin17cohort13[!(is.na(USin17cohort13$hhid)),]
USin17cohort13_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin17cohort13,na.rm=T)
svymean(USin17cohort13$FI, USin17cohort13_w, na.rm=T)
```

```{r}
USin17cohort12<- UNSR17[UNSR17$RESIDENCY==2012,]
USin17cohort12<- USin17cohort12[!(is.na(USin17cohort12$hhid)),]
USin17cohort12_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin17cohort12,na.rm=T)
svymean(USin17cohort12$FI, USin17cohort12_w, na.rm=T)
```
And 2016

```{r}
USin16cohort15<- UNSR16[UNSR16$RESIDENCY==2015,]
USin16cohort15<- USin16cohort15[!(is.na(USin16cohort15$hhid)),]
USin16cohort15_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin16cohort15,na.rm=T)
svymean(USin16cohort15$FI, USin16cohort15_w, na.rm=T)
```
```{r}
USin16cohort14<- UNSR16[UNSR16$RESIDENCY==2014,]
USin16cohort14<- USin16cohort14[!(is.na(USin16cohort14$hhid)),]
USin16cohort14_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin16cohort14,na.rm=T)
svymean(USin16cohort14$FI, USin16cohort14_w, na.rm=T)
```
```{r}
USin16cohort13<- UNSR16[UNSR16$RESIDENCY==2013,]
USin16cohort13<- USin16cohort13[!(is.na(USin16cohort13$hhid)),]
USin16cohort13_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin16cohort13,na.rm=T)
svymean(USin16cohort13$FI, USin16cohort13_w, na.rm=T)
```
```{r}
USin16cohort12<- UNSR16[UNSR16$RESIDENCY==2012,]
USin16cohort12<- USin16cohort12[!(is.na(USin16cohort12$hhid)),]
USin16cohort12_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin16cohort12,na.rm=T)
svymean(USin16cohort12$FI, USin16cohort12_w, na.rm=T)
```
```{r}
USin16cohort11<- UNSR16[UNSR16$RESIDENCY==2011,]
USin16cohort11<- USin16cohort11[!(is.na(USin16cohort11$hhid)),]
USin16cohort11_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin16cohort11,na.rm=T)
svymean(USin16cohort11$FD, USin16cohort11_w, na.rm=T)
```

# Now to seperate them male and female headed households (and use prettier and more consice code.)

```{r}
USin16cohort11<- UNSR16[UNSR16$RESIDENCY==2011 & UNSR16$SEX=="Male",]
USin16cohort11<- USin16cohort11[!(is.na(USin16cohort11$hhid)),]
USin16cohort11_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin16cohort11,na.rm=T)
svymean(USin16cohort11$FD, USin16cohort11_w, na.rm=T)
```

```{r}
f_d_16<- function(data=UNSR16){
    cohorts16<- list()
  cohorts16$cohort<-list()
  cohorts16$cohort<-split(data, data$RESIDENCY)
  cohorts16$by_sex<-list()
  for (i in seq_along(cohorts16$cohort)){
    each <- cohorts16$cohort[[i]]
    cohorts16$by_sex[[i]]<- split(each, each$SEX)
  }
  for (by_sex_list in cohorts16$by_sex){
      for (each in by_sex_list){
    design= svydesign(ids=~hhid, weights =~Weight_household,data = each,na.rm=T)
    holder<-svymean(each$FD, design = design, na.rm = T)
    cohorts16$means_by_sex<-append(cohorts16$means_by_sex, list(holder))
      }
    
  }
    for (each_cohort in list(cohorts16$cohort)){
      for(each in each_cohort){
    design= svydesign(ids=~hhid, weights =~Weight_household,data = each,na.rm=T)
    holder<-svymean(each$FD, design = design, na.rm = T)
    cohorts16$cohort_means<-append(cohorts16$cohort_means, list(holder))
      }
      }
    return(cohorts16)
    }
```


```{r}
f_d_16 <- function(data = UNSR16) {
  cohorts16 <- list()
  cohorts16$cohort <- split(data, data$WHENARRIVE)
  cohorts16$by_sex <- list()
  cohorts16$means_by_sex <- list()
  cohorts16$cohort_means <- list()
  
  # Naming the by_sex list
  for (i in seq_along(cohorts16$cohort)) {
    each <- cohorts16$cohort[[i]]
    cohorts16$by_sex[[i]] <- split(each, each$SEX)
    names(cohorts16$by_sex)[i] <- unique(each$WHENARRIVE)
  }
  
  # Calculating means by sex
  for (WHENARRIVE in names(cohorts16$by_sex)) {
    by_sex_list <- cohorts16$by_sex[[WHENARRIVE]]
    for (sex in names(by_sex_list)) {
      each <- by_sex_list[[sex]]
      design <- svydesign(ids = ~hhid, weights = ~Weight_household, data = each, na.rm = TRUE)
      holder <- svymean(~FD, design = design, na.rm = TRUE)
      cohorts16$means_by_sex[[paste(WHENARRIVE, sex, sep = "_")]] <- holder
    }
  }
  
  # Calculating means for each cohort
  for (WHENARRIVE in names(cohorts16$cohort)) {
    each <- cohorts16$cohort[[WHENARRIVE]]
    design <- svydesign(ids = ~hhid, weights = ~Weight_household, data = each, na.rm = TRUE)
    holder <- svymean(~FD, design = design, na.rm = TRUE)
    cohorts16$cohort_means[[WHENARRIVE]] <- holder
  }
  
  return(cohorts16)
}

```

```{r}
cohorts16<-f_d_16(data = UNSR16)
cohorts17<-f_d_16(data = UNSR17)
cohorts18<-f_d_16(data = UNSR18)
cohorts19<-f_d_16(data = UNSR19)

```


