---
title: "Thesis Work"
output: html_notebook
---

# Let's load in the data and packages

```{r}
library(janitor)
library(stargazer)
library(tidyverse)
library(mice)
library(DescTools)
library(survey)
library(lmtest)
library(naniar)
library(glue)
library(haven)
```

```{r}

UNASR16 <- read_dta("P:/Refugee Data/Combined ASR/2016/2016-ASR_Public_Use_File.dta")
#View(ASR16)


UNASR17 <- read_dta("P:/Refugee Data/Combined ASR/2017/2017 ASR_Public_Use_File.dta")
#View(ASR17)


UNASR18 <- read_dta("P:/Refugee Data/Combined ASR/2018/2018 ASR_Public_Use_File.dta")
#View(ASR18)


UNASR19 <- read_dta("P:/Refugee Data/Combined ASR/2019/2019 ASR_Public_Use_File.dta")
#View(ASR19)

UNASR20 <- read_dta("P:/Refugee Data/Combined ASR/2020/2020 ASR_Public_Use_File_correction_ver2.dta")

ind_data<-list(UNASR16, UNASR17, UNASR18, UNASR19)
ind_data<- lapply(ind_data, zap_labels)
ind_df_names<- c("UNASR16", "UNASR17", "UNASR18", "UNASR19")

names(ind_data) <- ind_df_names
```

I need a function to make better tables
```{r}
logit_results<-function(summary_object){
  output<-cbind.data.frame(summary_object$term, round(exp(summary_object$estimate),2), round(summary_object$p.value, 3))
  return(output)
}

```





Setting up weighted household level analysis

```{r}
UNSR16<- UNASR16[UNASR16$respondent==1,]
UNSR17<- UNASR17[UNASR17$respondent==1,]
UNSR18<- UNASR18[UNASR18$respondent==1,]
UNSR19<- UNASR19[UNASR19$respondent==1,]
UNSR20<- UNASR20[UNASR20$respondent==1,]

# Now a list of the household level data frames
hh_data<-list(UNSR16, UNSR17, UNSR18, UNSR19 )
hh_df_names<- c("UNASR16", "UNASR17", "UNASR18", "UNASR19")
names(hh_data) <- hh_df_names
hh_data<- lapply(hh_data, zap_labels)
match("Weight_household_R1", names(UNSR16))
match("Weight_household_R27", names(UNSR16))

match("Weight_household", names(UNSR16))

# I am making a list of all the columns related to my analysis here
#hhid,respondent, Weight_household_R1, Weight_household_R2, Weight_household_R3, Weight_household_R4, Weight_household_R5, Weight_household_R6, Weight_household_R7, Weight_household_R8, Weight_household_R9, Weight_household_R10, Weight_household_R11, Weight_household_R12, Weight_household_R13, Weight_household_R14, Weight_household_R15, Weight_household_R16, Weight_household_R17, Weight_household_R18, Weight_household_R19, Weight_household_R20, Weight_household_R21, Weight_household_R22, Weight_household_R23, Weight_household_R24, Weight_household_R25, Weight_household_R26, Weight_household_R27, FI, WHENJOB, WHENARRIVE, RESIDENCY,SEX,AGE,numppl,MARSTAT,DEPENDS, nothh_depends, KIDS,ORIGIN,ECOSECTOR,HOSTREG,SVYYR,HIGHEST_DEGREE, EDUC_YEARS, CONTEXT,PREENG,CURENGEN,CUREMPT,CURENG,URECOSEC, ui_soi_pubassist, TILLJOBb,WEEKHOUR, FOODSTAMPS, TANF, RCA, SSI, GA, Miscash, PubHo, NUM_PROGS
```

# Cleaning and Making Variables

## Making Time till First job

```{r}
# I think I can just make the 2020 data just look like the old stuff and then put it all through the same function. We get tripped up on small stuff like
years=list(2016, 2017, 2018, 2019)

# First the ES cleaning, because 2020 doesn't have first job.We have to separate ind level operations from hh level and ind is first
dc_2020_f<- function(hh_data, ind_data, years){
  # gotta uncomment this if yu wannd to timetilljob 
 # hh_data$WHENJOB<- hh_data$qn18dyear
#  hh_data$WHENJOB<- ifelse(is.na(hh_data$qn8year), 0, hh_data$qn18dyear)
  #Making a residency variable-- how long someone has been in US
  hh_data$RESIDENCY<-years-as.numeric(hh_data$qn8year)
  #When arrive is the year they arrive
  hh_data$WHENARRIVE<-as.numeric(hh_data$qn8year)
  ind_data$WHENARRIVE<-as.numeric(ind_data$qn8year)
  
  hh_data$WHENARRIVE<-ifelse(hh_data$qn8year==9999 |hh_data$qn8year==9998, NA, hh_data$qn8year)
  ind_data$WHENARRIVE<-ifelse(ind_data$qn8year==9999 |ind_data$qn8year==9998, NA, ind_data$qn8year)
  # Remove for 2020 tilljobb
  #hh_data$TILLJOBb<- hh_data$WHENJOB-hh_data$WHENARRIVE
  
 # hh_data<-hh_data%>%mutate(TILLJOBb= case_when(TILLJOBb<0 & TILLJOBb>-6~0,
 #                                                    TILLJOBb<=-100~6,
 #                                                   .default= TILLJOBb))
  
  
  
  #Making weekly working hours qn37=all jobs weekly working hours last week, qn43=weekly working hours last year, all jobs
  hh_data$qn6a<- ifelse(hh_data$qn37==98 | hh_data$qn37==99, NA, hh_data$qn37)
  hh_data$qn6b<- ifelse(hh_data$qn43==98 | hh_data$qn43==99, NA, hh_data$qn43)
  hh_data$WEEKHOUR<- hh_data$qn6b
  ## This is a little odd, but makes sure WEEKHOUR is not NA by using 6a if 6b is NA. 
  hh_data$WEEKHOUR<- ifelse(is.na(hh_data$WEEKHOUR), hh_data$qn6a, hh_data$qn6b)
  
  #Age and Kid variables
  hh_data$AGE<- ifelse(hh_data$qn4a==999|hh_data$qn4a==998, NA, hh_data$qn4a)
  ind_data$KID<- ifelse(ind_data$qn4a<16, 1, 0)
  
  #Education Vars
  hh_data$qn30<- ifelse(hh_data$qn30==99| hh_data$qn30==98| hh_data$qn30==97 | hh_data$qn30==90, NA, hh_data$qn30)
  hh_data<- hh_data%>% mutate(HIGHEST_DEGREE= case_when(qn30== 5~4,
                                                        qn30==4 |qn30 ==3~5,
                                                        qn30==7~6,
                                                        qn30==9~4,
                                                        .default=qn30))
  ind_data$qn30<- ifelse(ind_data$qn30==99| ind_data$qn30==98| ind_data$qn30==97 | ind_data$qn30==90, NA, ind_data$qn30)
  ind_data<- ind_data%>% mutate(HIGHEST_DEGREE= case_when(qn30== 5~4,
                                                        qn30==4 |qn30 ==3~5,
                                                        qn30==7~6,
                                                        qn30==9~4,
                                                        .default=qn30))
  
# This is for comparisons with earlier work  
    hh_data$HIGHEST_DEGREE<- factor(hh_data$HIGHEST_DEGREE,levels=1:7, labels = c("None", "Primary", "Camp Training", "Technical School", "Secondary", "University", "Medical Degree"))
    
    
#This is it's own system.     
#  hh_data$HIGEST_DEGREE<- factor(hh_data$HIGHEST_DEGREE,levels=1:9, labels = c("None", "Primary", "Middle", "Highschool", "Tech/Vocational", "Some University", "BA", "Advanced Degree", "Religious School"))

  
  #This gets the number of kids in a household. 
kids<- ind_data %>%
  filter(KID==1 )%>% group_by(hhid) %>% summarize(KIDS= sum(KID))

hh_data<- hh_data%>% left_join(kids, by= "hhid")
 
# Now lets do education of non household heads. Probably average years of education works best. We subset based on those who are nolder than 14 because FLSA #sets 14 as minimum age for employment (except in Ag, which is just a limitation.)
non_resp_educ<- ind_data %>% filter(respondent == 0 & qn4a>13 )%>% group_by(hhid) %>% summarize(NONRESP_MAX_DEGREE= max(HIGHEST_DEGREE))

hh_data<- hh_data%>% left_join(non_resp_educ, by= "hhid")

##2016
# Buissness Owner, Professional, management, and white collar will be a "Professional"
hh_data<- hh_data%>% mutate(ECOSECTOR= case_when(qn16>96~NA,
                                                 .default = qn16))
hh_data$ECOSECTOR<- factor(hh_data$ECOSECTOR, levels = c(1:4), labels = c("None", "working", "self-employed", "Other"))

hh_data$ECOSECTOR<-relevel(hh_data$ECOSECTOR, ref ="None")

#2020 has the job that they did right before they came to the US too. 

hh_data<- hh_data %>% mutate(before_US_job= case_when(qn19==98 | qn19== 99~NA, 
                                                      .default=qn19))

hh_data$before_US_job<- factor(hh_data$before_US_job, levels = c(1:4), labels = c("None", "working", "self-employed", "Other"))

hh_data$before_US_job<-relevel(hh_data$before_US_job, ref ="None")

# The current sector of employment doesn't exist in 2020. Instead we have ui_work

hh_data<- hh_data %>% mutate(US_work= case_when(ui_work==999~NA, 
                                                      .default=qn19))

hh_data$US_work<- factor(hh_data$US_work, levels = c(1:4), labels = c("None", "working", "self-employed", "Other"))

hh_data$US_work<-relevel(hh_data$US_work, ref ="None")



hh_data<- hh_data%>% mutate(ORIGIN =case_when(qn6==1|qn6==5|qn6==14|qn6==15|qn6==26~97, 
                                            qn6==96|qn6==98|qn6==99~NA, 
                                            .default = qn6))
hh_data$ORIGIN<- factor(hh_data$ORIGIN, levels = c(2,3,7,8,11,17,19,21,23,27,97), labels = c("Bhutan", "Burma", "DR Congo", "Eritrea", "Iraq",  "Somalia", "Syria", "Thailand", "Ukraine", "El Salvador", "Other"))
## This labels all of the countries of origin, which might not be very useful. It clogs up the regression output. 
##hh_data$ORIGIN<- factor(hh_data$ORIGIN, levels = c(1,3:5,7,8,11,14:17,19,21,23,26,27,9797), labels = c("US","Bhutan", "Burma", "Burundi", "DR Congo", "Eritrea", "Iraq", "Malaysia", "Nepal", "Rwanada",  "Somalia", "Syria", "Thailand", "Ukraine", "Colombia", "El Salvador", "Other"))
hh_data$ORIGIN<-relevel(hh_data$ORIGIN,ref = "Iraq")

# Pre migration English proficiency
hh_data$qnqn23<- ifelse(hh_data$qn23== 8|hh_data$qn23==9, NA, hh_data$qn23)
hh_data$PREENG<- abs(hh_data$qn23-5)
#Region of resettlement
hh_data$HOSTREG<-ifelse(hh_data$qn9==98| hh_data$qn9==99, NA, hh_data$qn9)

hh_data$HOSTREG<- factor(hh_data$HOSTREG,levels = c(1,2,3,4),labels = c("NorthEast", "South", "MidWest", "West"))
hh_data$HOSTREG<-relevel(hh_data$HOSTREG, ref = 4)
#Current enrollment in a English  program
hh_data$CURENGEN<- ifelse(hh_data$qn25>3, NA, ifelse(hh_data$qn25==2, 0, hh_data$qn25))
#Factorize
hh_data$CURENGEN<- factor(hh_data$CURENGEN, levels = c(0,1), labels = c("No", "Yes"))

#Current enrollment in a job training program
hh_data$CUREMPT<- ifelse(hh_data$qn28==8|hh_data$qn28==9, NA, hh_data$qn28)
#Factorize
hh_data$CUREMPT<- factor(hh_data$CUREMPT, levels = c(1,2), labels = c("Yes", "No"))

#English proficiency now
hh_data$qn24<- ifelse(hh_data$qn24==8|hh_data$qn24==9, NA, hh_data$qn24)
hh_data$CURENG<- abs(hh_data$qn24-5)

#Factorizing
hh_data$CURENG<- factor(hh_data$CURENG,levels = c(1,2,3,4), labels = c("Not at All", "Not Well", "Well", "Very Well"), ordered = F)
# Sex
hh_data$SEX<- ifelse(hh_data$qn3>89, NA, hh_data$qn3)

ind_data$SEX<- ifelse(ind_data$qn3>89, NA, ind_data$qn3)

# Factorize
ind_data$SEX<- factor(ind_data$SEX, levels = c(1,2),labels = c("Male", "Female"))
# Factorize
hh_data$SEX<- factor(hh_data$SEX, levels = c(1,2),labels = c("Male", "Female"))

# Marital Status

hh_data<- hh_data%>% mutate(MARSTAT= case_when(qn5==2~1,
                                               qn5==5~3,
                                               qn5==96| qn5>97~NA,
                                               .default=qn5))


# FActorizing

hh_data$MARSTAT<- factor(hh_data$MARSTAT, levels = c(1,2,3,4,5), labels = c("Married", "Divorced/Seperated/Widowed", "Never Married", "Other", "R is a child"))

# The dependets variable
ind_data$DEPENDS<- ifelse(ind_data$qn20==4,1,0)

nothh_depends<- ind_data %>%
  filter(respondent==0 )%>% group_by(hhid) %>% summarize(nothh_depends= sum(DEPENDS))

hh_data<- hh_data%>% left_join(nothh_depends, by= "hhid")

#Now need to do household is dependent
hh_data$hh_DEPENDS<- ifelse(hh_data$qn20==4,1,0)

hh_data$SVYYR<- years

#Dependence on pub assist programs. 

## Food Stamps
hh_data<-hh_data%>% mutate(Foodstamps= case_when(qn60==2~0,
                                                 qn60>2~NA,
                                                 .default=qn60))
hh_data$Foodstamps<-factor(hh_data$Foodstamps,levels = c(0,1), labels = c(" Not On Foodstamps", "On foodstamps"))

#Tanf
hh_data<-hh_data%>% mutate(TANF= case_when(qn61==2~0,
                                                 qn61>2~NA,
                                                 .default=qn61))

#Factorizing
hh_data$TANF<-factor(hh_data$TANF,levels = c(0,1), labels = c(" Not On TANF", "On TANF"))

# SSI
hh_data<-hh_data%>% mutate(SSI= case_when(qn62==2~0,
                                                 qn62>2~NA,
                                                 .default=qn62))

#Factorizing
hh_data$SSI<-factor(hh_data$SSI,levels = c(0,1), labels = c(" Not On SSI", "On SSI"))

#General Assistance

hh_data<-hh_data%>% mutate(GA= case_when(qn63==2~0,
                                                 qn63>2~NA,
                                                 .default=qn63))

#Factorizing
hh_data$GA<-factor(hh_data$GA,levels = c(0,1), labels = c(" Not On GA", "On GA"))

#Other assistance Includes things like public housing or help with bills
hh_data<-hh_data%>% mutate(Miscash= case_when(qn64==2~0,
                                                 qn64>2~NA,
                                                 .default=qn64))

#Factorizing
hh_data$Miscash<-factor(hh_data$Miscash,levels = c(0,1), labels = c(" Not On Miscash", "On Miscash"))











# DEPENDENCE FOR IND_DATA
#Dependence on pub assist programs. 

## Food Stamps
ind_data<-ind_data%>% mutate(Foodstamps= case_when(qn60==2~0,
                                                 qn60>2~NA,
                                                 .default=qn60))
ind_data$Foodstamps<-factor(ind_data$Foodstamps,levels = c(0,1), labels = c(" Not On Foodstamps", "On foodstamps"))

#Tanf
ind_data<-ind_data%>% mutate(TANF= case_when(qn61==2~0,
                                                 qn61>2~NA,
                                                 .default=qn61))

#Factorizing
ind_data$TANF<-factor(ind_data$TANF,levels = c(0,1), labels = c(" Not On TANF", "On TANF"))

# SSI
ind_data<-ind_data%>% mutate(SSI= case_when(qn62==2~0,
                                                 qn62>2~NA,
                                                 .default=qn62))

#Factorizing
ind_data$SSI<-factor(ind_data$SSI,levels = c(0,1), labels = c(" Not On SSI", "On SSI"))

#General Assistance

ind_data<-ind_data%>% mutate(GA= case_when(qn63==2~0,
                                                 qn63>2~NA,
                                                 .default=qn63))

#Factorizing
ind_data$GA<-factor(ind_data$GA,levels = c(0,1), labels = c(" Not On GA", "On GA"))

#Other assistance Includes things like public housing or help with bills
ind_data<-ind_data%>% mutate(Miscash= case_when(qn64==2~0,
                                                 qn64>2~NA,
                                                 .default=qn64))

#Factorizing
ind_data$Miscash<-factor(ind_data$Miscash,levels = c(0,1), labels = c(" Not On Miscash", "On Miscash"))














hh_data$NUM_PROGS <- as.numeric(hh_data$Foodstamps)+as.numeric(hh_data$TANF)+as.numeric(hh_data$SSI)+as.numeric(hh_data$GA)+as.numeric(hh_data$Miscash)-5
ind_data$NUM_PROGS<-as.numeric(ind_data$Foodstamps)+as.numeric(ind_data$TANF)+as.numeric(ind_data$SSI)+as.numeric(ind_data$GA)+as.numeric(ind_data$Miscash)-5
# A Dichotomous Financial Independence
hh_data<-hh_data %>% mutate(FD=case_when(NUM_PROGS==0~0,
                               NUM_PROGS>0~1))

ind_data<-ind_data %>% mutate(FD=case_when(NUM_PROGS==0~0,
                               NUM_PROGS>0~1))

  hh_data<- hh_data%>% mutate(ui_soi_pubassist= case_when(qn57>800 & NUM_PROGS!=0~2,
                                                          qn57<800 & NUM_PROGS==0~1,
                                                          qn57>800 & NUM_PROGS!=0~3,
                                                          qn57<800 & NUM_PROGS==0~4,
                                                          NUM_PROGS!=0 & is.na(qn57)~5,
                                                          qn57>800 & is.na(NUM_PROGS)~6,
                                                          NUM_PROGS==0 & is.na(qn57)~7,
                                                          is.na(NUM_PROGS) & is.na(qn57)~999))
  
  ind_data<- ind_data%>% mutate(ui_soi_pubassist= case_when(qn57>800 & NUM_PROGS!=0~2,
                                                          qn57<800 & NUM_PROGS==0~1,
                                                          qn57>800 & NUM_PROGS!=0~3,
                                                          qn57<800 & NUM_PROGS==0~4,
                                                          NUM_PROGS!=0 & is.na(qn57)~5,
                                                          qn57>800 & is.na(NUM_PROGS)~6,
                                                          NUM_PROGS==0 & is.na(qn57)~7,
                                                          is.na(NUM_PROGS) & is.na(qn57)~999))
                              
                                                
  hh_data$FI<- ifelse(hh_data$ui_soi_pubassist==999, NA, ifelse(hh_data$ui_soi_pubassist==1, 0,1))
  ind_data$FI<- ifelse(ind_data$ui_soi_pubassist==999, NA, ifelse(ind_data$ui_soi_pubassist==1, 0,1))
#Don't forget to add TILLJOBb & WHENJOB back in 
  
hh_data$in_df<-1
ind_data$in_df<-1
# Now to filter the dataset. 
hh_df<- hh_data %>% select(hhid,respondent,in_df,  Weight_household,Weight_household_pop,Weight_person_pop, FI, FD, WHENARRIVE, RESIDENCY,SEX,AGE,numppl,MARSTAT,hh_DEPENDS, nothh_depends, KIDS,ORIGIN,ECOSECTOR,HOSTREG,SVYYR,HIGHEST_DEGREE, NONRESP_MAX_DEGREE,PREENG,CURENGEN,CUREMPT,CURENG, ui_soi_pubassist,WEEKHOUR, Foodstamps, TANF, SSI, GA, Miscash, NUM_PROGS)

ind_df<- ind_data %>% select(hhid,respondent,in_df,WHENARRIVE, Weight_household,Weight_person_pop, Weight_household_pop, numppl, SEX, FI, FD) %>% dplyr::filter( !is.na(Weight_person_pop))


#Let's do the imputations

#Probably want to name them before we return the data




return(list(hh_df, ind_df))}

data_2020<-dc_2020_f(UNSR20, UNASR20, years=2020)
names(data_2020)<- c("UNSR2020", "UNASR2020")
```


```{r}
# First the ES cleaning, because 2020 doesn't have first job.We have to separate ind level operations from hh level and ind is first
first_job_f<- function(hh_data, ind_data, years){

  hh_data$WHENJOB<- hh_data$qn18dyear
  hh_data$WHENJOB<- ifelse(is.na(hh_data$qn18dyear), 0, hh_data$qn18dyear)
  
  # we should make a individual level when job
  
  ind_data$WHENJOB<- ind_data$qn18dyear
  ind_data$WHENJOB<- ifelse(is.na(ind_data$qn18dyear), 0, ind_data$qn18dyear)
  
  
  #Making a residency variable-- how long someone has been in US
  hh_data$RESIDENCY<-years-as.numeric(hh_data$qn1jyear)
  #When arrive is the year they arrive
  hh_data$WHENARRIVE<-as.numeric(hh_data$qn1jyear)
  ind_data$WHENARRIVE<-as.numeric(ind_data$qn1jyear)
  
  ind_data$TILLJOBb<- ind_data$WHENJOB-ind_data$WHENARRIVE
  
  ind_data<-ind_data%>%mutate(TILLJOBb= case_when(TILLJOBb<0 & TILLJOBb>-6~0,
                                                    TILLJOBb<=-100~6,
                                                   .default= TILLJOBb))
  min_first_job<- ind_data %>% group_by(hhid) %>% summarize(min_first_job = min(TILLJOBb))
  hh_data<- hh_data%>% left_join(min_first_job, by= "hhid")
  
  hh_data$TILLJOBb<- hh_data$min_first_job
                                                
  hh_data$FI<- ifelse(hh_data$ui_soi_pubassist==999, NA, ifelse(hh_data$ui_soi_pubassist==1, 0,1))
  ind_data$FI<- ifelse(ind_data$ui_soi_pubassist==999, NA, ifelse(ind_data$ui_soi_pubassist==1, 0,1))
  #Making weekly working hours 6a=primary job, 6b=all jobs
  hh_data$qn6a<- ifelse(hh_data$qn6a==98 | hh_data$qn6a==99, NA, hh_data$qn6a)
  hh_data$qn6b<- ifelse(hh_data$qn6b==98 | hh_data$qn6b==99, NA, hh_data$qn6b)
  hh_data$WEEKHOUR<- hh_data$qn6b
  ## This is a little odd, but makes sure WEEKHOUR is not NA by using 6a if 6b is NA. 
  hh_data$WEEKHOUR<- ifelse(is.na(hh_data$WEEKHOUR), hh_data$qn6a, hh_data$qn6b)
  
  #Age and Kid variables
  hh_data$AGE<- ifelse(hh_data$qn1d==999|hh_data$qn1d==998, NA, hh_data$qn1d)
  ind_data$KID<- ifelse(ind_data$qn1d<16, 1, 0)
  
  #Education Vars
  hh_data$qn2b<- ifelse(hh_data$qn2b==99| hh_data$qn2b==98| hh_data$qn2a==97, NA, hh_data$qn2b)
  hh_data$HIGHEST_DEGREE<- hh_data$qn2b
  hh_data$HIGEST_DEGREE<- factor(hh_data$HIGHEST_DEGREE,levels=1:7, labels = c("None", "Primary", "Camp Training", "Technical School Cert", "Secondary", "University", "Medical Degree"))
  hh_data$EDUC_YEARS<- ifelse(hh_data$qn2a==99| hh_data$qn2a==98, NA, hh_data$qn2a)
  ind_data$EDUC_YEARS<- ifelse(ind_data$qn2a==99| ind_data$qn2a==98, NA, ind_data$qn2a)
  
  #This gets the number of kids in a household. 
kids<- ind_data %>%
  filter(KID==1 )%>% group_by(hhid) %>% summarize(KIDS= sum(KID))

hh_data<- hh_data%>% left_join(kids, by= "hhid")
 
 # Now lets do education of non household heads. Probably average years of education works best. We subset based on those who are nolder than 14 because FLSA sets 14 as minimum age for employment (except in Ag, which is just a limitation.)
non_resp_educ<- ind_data %>%
  filter(respondent == 0 & qn1d>13 )%>% group_by(hhid) %>% summarize(NONRESP_EDUC_YEARS= mean(EDUC_YEARS))

hh_data<- hh_data%>% left_join(non_resp_educ, by= "hhid")

#this is previous sector of employment
hh_data$qn3b<- ifelse(hh_data$qn3b==98|hh_data$qn3b== 99, NA, hh_data$qn3b)

##2016
# Buissness Owner, Professional, management, and white collar will be a "Professional"
hh_data$ECOSECTOR<- ifelse(hh_data$qn3b == 1| hh_data$qn3b == 2|hh_data$qn3b ==3|hh_data$qn3b ==4|hh_data$qn3b ==5, 1, 
      #Sales will be Sales                    
                  ifelse(hh_data$qn3b ==6, 2, 
                          #Hospitality, service workers, and laborers will be "Service"       
                                 ifelse(hh_data$qn3b ==9|hh_data$qn3b ==10|hh_data$qn3b ==11, 3, 
                                        #Skilled Trades will be "Blue Collar"
                                        ifelse(hh_data$qn3b ==7|hh_data$qn3b ==8|hh_data$qn3b ==12, 4, 
                 #None is none
                 ifelse(hh_data$qn3b ==96, 0, 
                        #Students are students
                        ifelse(hh_data$qn3b ==13, 5, 
                 #Other is other
                 ifelse(hh_data$qn3b== 97, 6, hh_data$qn3b)))))))
hh_data$ECOSECTOR<- factor(hh_data$ECOSECTOR, levels = c(0:6), labels = c("None","Professional", "Sales", "Service", "Blue Collar", "Student", "Other"))

hh_data$ECOSECTOR<-relevel(hh_data$ECOSECTOR, ref ="None")

# The current sector of employment
hh_data$URECOSEC<-ifelse(hh_data$qn19b==99|hh_data$qn19b==98,NA,
                        #Blue Collar
                        ifelse(hh_data$qn19b==1|hh_data$qn19b==8|hh_data$qn19b==10, 1, 
                               
                  #Retail/Service
                  
                   ifelse(hh_data$qn19b==2|hh_data$qn19b==5|hh_data$qn19b==7|hh_data$qn19b==11, 2, 
                             ifelse(hh_data$qn19b==4|hh_data$qn19b==3, 3, 
                                    
                                    #General logistics
                                    
                                  ifelse(hh_data$qn19b==9|hh_data$qn19b==6|hh_data$qn19b==12, 4, 
                                           ifelse(hh_data$qn19b==97, 5 ,
                                                  ifelse(hh_data$qn19b==96, 0,hh_data$qn19b)))))))
#Factorize Current Sector of employment
hh_data$URECOSEC<- factor(hh_data$URECOSEC, labels= c("None", "BlueCollar", "Retail/Sales", "Professional/ED/Health/SocialServices", "General Logistical Support", "Other"), levels = c(0:5), ordered = F)
#Country of Origin
hh_data<- hh_data%>% mutate(ORIGIN =case_when(qn1g==1|qn1g==4|qn1g==7|qn1g==11|qn1g==12|qn1g==13|qn1g==15|qn1g==19|qn1g==21| qn1g==24| qn1g==25~97, 
                                            qn1g==96|qn1g==98|qn1g==99~NA, 
                                            .default = qn1g))
hh_data$ORIGIN<- factor(hh_data$ORIGIN, levels = c(2:3,5:6,9:10, 16, 18,20, 22,26, 97), labels = c("Bhutan", "Burma", "Cuba", "DR Congo", "Iran", "Iraq",  "Somalia", "Syria", "Thailand", "Ukraine", "El Salvador", "Other"))
## This labels all of the countries of origin, which might not be very useful. It clogs up the regression output. 
#hh_data$ORIGIN<- factor(hh_data$ORIGIN,levels = c(1:22,24:26, 97), labels = c("Afghanistan", "Bhutan", "Burma","Burundi", "Cuba", "DR Congo", "Eritrea", "Ethiopia", "Iran", "Iraq", "Jordan", "Kenya", "Malaysia", "Nepal", "Rwanada", "Somalia", "Sudan", "Syria", "Tanzania", "Thailand", "Uganda",  "Ukraine", "U.S.", "Colombia", "El Salvador", "Other"))
hh_data$ORIGIN<-relevel(hh_data$ORIGIN,ref = "Cuba")

# The contextual attainment
### Making country specific variance estimates. All estimates use the UN Development Program Human Development report for 2015 or the most recently available data (for Somalia): https://hdr.undp.org/en/indicators/103006. These are just raw deviations from the mean. 
#Bhutan Mean for 2015 Mean =3.4 
hh_data$CONTEXT<- ifelse(hh_data$ORIGIN== "Afghanistan", hh_data$EDUC_YEARS-2.37, 
                        ifelse(hh_data$ORIGIN== "Bhutan", hh_data$EDUC_YEARS-3.4, 
                        ifelse(hh_data$ORIGIN=="Burma", hh_data$EDUC_YEARS-4.9, ifelse(hh_data$ORIGIN=="Burundi", hh_data$EDUC_YEARS-2.29,
                              ifelse(hh_data$ORIGIN=="Cuba", hh_data$EDUC_YEARS-11.4,
                                      ifelse(hh_data$ORIGIN=="DR Congo", hh_data$EDUC_YEARS-6.4,
                                             ifelse(hh_data$ORIGIN=="Eritrea", hh_data$EDUC_YEARS-3.9,
                                                    ifelse(hh_data$ORIGIN=="Ethiopia", hh_data$EDUC_YEARS-2.58,
                                                    ifelse(hh_data$ORIGIN=="Iran", hh_data$EDUC_YEARS-9.9, 
                                                           ifelse(hh_data$ORIGIN=="Iraq", hh_data$EDUC_YEARS-6.8, ifelse(hh_data$ORIGIN=="Jordan", hh_data$EDUC_YEARS-10.07,ifelse(hh_data$ORIGIN=="Kenya", hh_data$EDUC_YEARS-6.3, ifelse(hh_data$ORIGIN=="Malaysia", hh_data$EDUC_YEARS-10.23, ifelse(hh_data$ORIGIN=="Nepal", hh_data$EDUC_YEARS-4.5, ifelse(hh_data$ORIGIN=="Rwanada", hh_data$EDUC_YEARS-4.13,
                                                                  ifelse(hh_data$ORIGIN=="Somalia", hh_data$EDUC_YEARS-2.1, ifelse(hh_data$ORIGIN=="Sudan", hh_data$EDUC_YEARS-3.62,
                                                                         ifelse(hh_data$ORIGIN=="Syria", hh_data$EDUC_YEARS-5.1, ifelse(hh_data$ORIGIN=="Tanzania", hh_data$EDUC_YEARS-5.83, ifelse(hh_data$ORIGIN=="Thailand", hh_data$EDUC_YEARS-8.18, ifelse(hh_data$ORIGIN=="Uganda", hh_data$EDUC_YEARS-5.51,
                                                                              ifelse(hh_data$ORIGIN=="Ukraine", hh_data$EDUC_YEARS-11.4, 
                                                                                       ifelse(hh_data$ORIGIN=="U.S.", hh_data$EDUC_YEARS-13.3,ifelse(hh_data$ORIGIN=="Colombia", hh_data$EDUC_YEARS-8.05, ifelse(hh_data$ORIGIN=="El Salvador", hh_data$EDUC_YEARS-6.62, NA)))))))))))))))))))))))))

# Pre migration English proficiency
hh_data$qn4a<- ifelse(hh_data$qn4a== 8|hh_data$qn4a==9, NA, hh_data$qn4a)
hh_data$PREENG<- abs(hh_data$qn4a-5)
#Region of resettlement
hh_data$HOSTREG<-ifelse(hh_data$qn1k==98| hh_data$qn1k==99, NA, hh_data$qn1k)

hh_data$HOSTREG<- factor(hh_data$HOSTREG,levels = c(1,2,3,4),labels = c("NorthEast", "South", "MidWest", "West"))
hh_data$HOSTREG<-relevel(hh_data$HOSTREG, ref = 4)
#Current enrollment in a English  program
hh_data$CURENGEN<- ifelse(hh_data$qn4e==8|hh_data$qn4e==9, NA, ifelse(hh_data$qn4e==6, 2, hh_data$qn4e))
#Factorize
hh_data$CURENGEN<- factor(hh_data$CURENGEN, levels = c(1,2), labels = c("No", "Yes"))

#Current enrollement in a job training program
hh_data$CUREMPT<- ifelse(hh_data$qn24a==8|hh_data$qn24a==9, NA, hh_data$qn24a)
#Factorize
hh_data$CUREMPT<- factor(hh_data$CUREMPT, levels = c(1,2), labels = c("No", "Yes"))

#English proficiency now
hh_data$qn4b<- ifelse(hh_data$qn4b==8|hh_data$qn4b==9, NA, hh_data$qn4b)
hh_data$CURENG<- abs(hh_data$qn4b-5)

#Factorizing
hh_data$CURENG<- factor(hh_data$CURENG,levels = c(1,2,3,4), labels = c("Not at All", "Not Well", "Well", "Very Well"), ordered = F)
# Sex
hh_data$SEX<- ifelse(hh_data$qn1f==8|hh_data$qn1f==9, NA, hh_data$qn1f)

ind_data$SEX<- ifelse(ind_data$qn1f==8|ind_data$qn1f==9, NA, ind_data$qn1f)

# Factorize
ind_data$SEX<- factor(ind_data$SEX, levels = c(1,2),labels = c("Male", "Female"))

# Factorize
hh_data$SEX<- factor(hh_data$SEX, levels = c(1,2),labels = c("Male", "Female"))

# Marital Status

hh_data$MARSTAT<-ifelse(hh_data$qn1c== 8|hh_data$qn1c== 9, NA, 
                       ifelse(hh_data$qn1c== 2|hh_data$qn1c== 3|hh_data$qn1c== 5, 2, 
                              ifelse(hh_data$qn1c== 4, 3,
                                     ifelse(hh_data$qn1c== 7, 4,
                                            ifelse(hh_data$qn1c== 6, 5, hh_data$qn1c)))))


# FActorizing

hh_data$MARSTAT<- factor(hh_data$MARSTAT, levels = c(1,2,3,4,5), labels = c("Married", "Divorced/Seperated/Widowed", "Never Married", "Other", "R is a child"))

# The dependets variable
ind_data$DEPENDS<- ifelse(ind_data$qn28a== 8|ind_data$qn28a== 9, NA, 
                       ifelse(ind_data$qn28a== 1, 0, 
                              ifelse(ind_data$qn28a== 2, 1, ind_data$qn28a)))

nothh_depends<- ind_data %>%
  filter(respondent==0 )%>% group_by(hhid) %>% summarize(nothh_depends= sum(DEPENDS))

hh_data<- hh_data%>% left_join(nothh_depends, by= "hhid")

#Now need to do household is dependent
hh_data$hh_DEPENDS<- ifelse(hh_data$qn28a== 8|hh_data$qn28a== 9, NA, 
                       ifelse(hh_data$qn28a== 1, 0, 
                              ifelse(hh_data$qn28a== 2, 1, hh_data$qn28a)))

hh_data$SVYYR<- years

#Dependence on pub assist programs. 

## Food Stamps
hh_data<-hh_data%>% mutate(Foodstamps= case_when(qn30a==1~0,
                                               qn30a==2~1,
                                               qn30a==8~as.numeric(NA),
                                               qn30a==9~as.numeric(NA)))
hh_data$Foodstamps<-factor(hh_data$Foodstamps,levels = c(0,1), labels = c(" Not On Foodstamps", "On foodstamps"))

#Tanf
hh_data<-hh_data%>% mutate(TANF= case_when(qn31a==1~0,
                                               qn31a==2~1,
                                               qn31a==8~as.numeric(NA),
                                               qn31a==9~as.numeric(NA)))

#Factorizing
hh_data$TANF<-factor(hh_data$TANF,levels = c(0,1), labels = c(" Not On TANF", "On TANF"))
# Refugee Cash Assistance
hh_data<-hh_data%>% mutate(RCA= case_when(qn32a==1~0,
                                               qn32a==2~1,
                                               qn32a==8~as.numeric(NA),
                                               qn32a==9~as.numeric(NA)))

#Factorizing
hh_data$RCA<-factor(hh_data$RCA,levels = c(0,1), labels = c(" Not On RCA", "On RCA"))

# SSI
hh_data<-hh_data%>% mutate(SSI= case_when(qn32a==1~0,
                                               qn33a==2~1,
                                               qn33a==8~as.numeric(NA),
                                               qn33a==9~as.numeric(NA)))


#Factorizing
hh_data$SSI<-factor(hh_data$SSI,levels = c(0,1), labels = c(" Not On SSI", "On SSI"))

#General Assistance

hh_data<-hh_data%>% mutate(GA= case_when(qn34a==1~0,
                                               qn34a==2~1,
                                               qn34a==8~as.numeric(NA),
                                               qn34a==9~as.numeric(NA)))

#Factorizing
hh_data$GA<-factor(hh_data$GA,levels = c(0,1), labels = c(" Not On GA", "On GA"))

#Other assistance
hh_data<-hh_data%>% mutate(Miscash= case_when(qn35a==1~0,
                                               qn35a==2~1,
                                               qn35a==8~as.numeric(NA),
                                               qn35a==9~as.numeric(NA)))

#Factorizing
hh_data$Miscash<-factor(hh_data$Miscash,levels = c(0,1), labels = c(" Not On Miscash", "On Miscash"))
#Public Housing
hh_data<-hh_data%>% mutate(PubHo= case_when(qn38c==1~0,
                                               qn38c==2~1,
                                               qn38c==8~as.numeric(NA),
                                               qn38c==9~as.numeric(NA)))

#Factorizing
hh_data$PubHo<-factor(hh_data$PubHo,levels = c(0,1), labels = c(" Not On PubHo", "On PubHo"))
# Number of Programs

hh_data$NUM_PROGS <- as.numeric(hh_data$Foodstamps)+as.numeric(hh_data$TANF)+as.numeric(hh_data$RCA)+as.numeric(hh_data$SSI)+as.numeric(hh_data$GA)+as.numeric(hh_data$Miscash)+as.numeric(hh_data$PubHo)-7
# A Dichotomous Financial Independence
hh_data<-hh_data %>% mutate(FD=case_when(NUM_PROGS==0~0,
                               NUM_PROGS>0~1))



## FD FOR THE IND_DATA

## Food Stamps
ind_data<-ind_data%>% mutate(Foodstamps= case_when(qn30a==1~0,
                                               qn30a==2~1,
                                               qn30a==8~as.numeric(NA),
                                               qn30a==9~as.numeric(NA)))
ind_data$Foodstamps<-factor(ind_data$Foodstamps,levels = c(0,1), labels = c(" Not On Foodstamps", "On foodstamps"))

#Tanf
ind_data<-ind_data%>% mutate(TANF= case_when(qn31a==1~0,
                                               qn31a==2~1,
                                               qn31a==8~as.numeric(NA),
                                               qn31a==9~as.numeric(NA)))

#Factorizing
ind_data$TANF<-factor(ind_data$TANF,levels = c(0,1), labels = c(" Not On TANF", "On TANF"))
# Refugee Cash Assistance
ind_data<-ind_data%>% mutate(RCA= case_when(qn32a==1~0,
                                               qn32a==2~1,
                                               qn32a==8~as.numeric(NA),
                                               qn32a==9~as.numeric(NA)))

#Factorizing
ind_data$RCA<-factor(ind_data$RCA,levels = c(0,1), labels = c(" Not On RCA", "On RCA"))

# SSI
ind_data<-ind_data%>% mutate(SSI= case_when(qn32a==1~0,
                                               qn33a==2~1,
                                               qn33a==8~as.numeric(NA),
                                               qn33a==9~as.numeric(NA)))


#Factorizing
ind_data$SSI<-factor(ind_data$SSI,levels = c(0,1), labels = c(" Not On SSI", "On SSI"))

#General Assistance

ind_data<-ind_data%>% mutate(GA= case_when(qn34a==1~0,
                                               qn34a==2~1,
                                               qn34a==8~as.numeric(NA),
                                               qn34a==9~as.numeric(NA)))

#Factorizing
ind_data$GA<-factor(ind_data$GA,levels = c(0,1), labels = c(" Not On GA", "On GA"))

#Other assistance
ind_data<-ind_data%>% mutate(Miscash= case_when(qn35a==1~0,
                                               qn35a==2~1,
                                               qn35a==8~as.numeric(NA),
                                               qn35a==9~as.numeric(NA)))

#Factorizing
ind_data$Miscash<-factor(ind_data$Miscash,levels = c(0,1), labels = c(" Not On Miscash", "On Miscash"))
#Public Housing
ind_data<-ind_data%>% mutate(PubHo= case_when(qn38c==1~0,
                                               qn38c==2~1,
                                               qn38c==8~as.numeric(NA),
                                               qn38c==9~as.numeric(NA)))

#Factorizing
ind_data$PubHo<-factor(ind_data$PubHo,levels = c(0,1), labels = c(" Not On PubHo", "On PubHo"))
# Number of Programs

ind_data$NUM_PROGS <- as.numeric(ind_data$Foodstamps)+as.numeric(ind_data$TANF)+as.numeric(ind_data$RCA)+as.numeric(ind_data$SSI)+as.numeric(ind_data$GA)+as.numeric(ind_data$Miscash)+as.numeric(ind_data$PubHo)-7
# A Dichotomous Financial Independence
ind_data<-ind_data %>% mutate(FD=case_when(NUM_PROGS==0~0,
                               NUM_PROGS>0~1))


hh_data$in_df<-1
ind_data$in_df<-1


# Now to filter the dataset. 
hh_df<- hh_data %>% select(hhid,respondent,in_df, Weight_household,Weight_household_pop,Weight_person_pop, FI, FD, WHENARRIVE, WHENJOB, RESIDENCY,SEX,AGE,numppl,MARSTAT,hh_DEPENDS, nothh_depends, KIDS,ORIGIN,ECOSECTOR,HOSTREG,SVYYR,HIGHEST_DEGREE, EDUC_YEARS, NONRESP_EDUC_YEARS, CONTEXT,PREENG,CURENGEN,CUREMPT,CURENG,URECOSEC, ui_soi_pubassist,WEEKHOUR, Foodstamps, TANF, RCA, SSI, GA, Miscash, PubHo, TILLJOBb, NUM_PROGS)


ind_df<- ind_data %>% select(hhid,respondent,in_df, Weight_household,Weight_person_pop,Weight_household_pop, FI, FD, SEX,numppl, WHENARRIVE, WHENJOB) %>% dplyr::filter( !is.na(Weight_person_pop))

#Let's do the imputations

#Probably want to name them before we return the data




return(list(hh_df, ind_df))
}
m_l<-Map(function(hh_data, ind_data, years) first_job_f(hh_data, ind_data, years), hh_data, ind_data, years)

master_list<- c(m_l, c(data_2020))

```


```{r}
f_d_16 <- function(data = UNSR16, i_data) {
  cohorts16 <- list()
  icohorts16<-list()
  cohorts16$cohort <- split(data, data$WHENARRIVE)
  icohorts16$cohort <- split(i_data, i_data$WHENARRIVE)
  cohorts16$by_sex <- list()
  cohorts16$means_by_sex <- list()
  cohorts16$cohort_means <- list()
  
  # Naming the by_sex list
  for (i in seq_along(cohorts16$cohort)) {
    each <- cohorts16$cohort[[i]]
    cohorts16$by_sex[[i]] <- split(each, each$SEX)
    names(cohorts16$by_sex)[i] <- unique(each$WHENARRIVE)
  }
  
  for (i in seq_along(icohorts16$cohort)) {
    each <- icohorts16$cohort[[i]]
    icohorts16$by_sex[[i]] <- split(each, each$SEX)
    names(icohorts16$by_sex)[i] <- unique(each$WHENARRIVE)
  }
  
  # Calculating means by sex
  for (WHENARRIVE in names(cohorts16$by_sex)) {
    by_sex_list <- cohorts16$by_sex[[WHENARRIVE]]
    for (sex in names(by_sex_list)) {
      each <- by_sex_list[[sex]]
      design <- svydesign(ids = ~hhid, weights = ~Weight_household, data = each, na.rm = TRUE)
      holder <- svymean(~FD, design = design, na.rm = TRUE)
      cohorts16$means_by_sex[[paste(WHENARRIVE, sex, sep = "_")]] <- holder
    }
  }
  
  # Calculating means for each cohort
  for (WHENARRIVE in names(cohorts16$cohort)) {
    each <- cohorts16$cohort[[WHENARRIVE]]
    design <- svydesign(ids = ~hhid, weights = ~Weight_household, data = each, na.rm = TRUE)
    holder <- svymean(~FD, design = design, na.rm = TRUE)
    cohorts16$cohort_means[[WHENARRIVE]] <- holder
  }
  
  #I want to get the weighted n's for each group
    for (WHENARRIVE in names(cohorts16$by_sex)) {
    w_n_list <- cohorts16$by_sex[[WHENARRIVE]]
    for (sex in names(w_n_list)) {
      each <- w_n_list[[sex]]
      design <- svydesign(ids = ~hhid, weights = ~Weight_household_pop, data = each, na.rm = TRUE)
      holder <- svytotal(~in_df, design = design, na.rm = TRUE)
      cohorts16$w_n_list[[paste(WHENARRIVE, sex, sep = "_")]] <- holder
    }
  }
  
  return(cohorts16)
}

```

```{r}
cohorts16<-f_d_16(data = master_list$UNASR16[[1]],master_list$UNASR16[[2]])
cohorts17<-f_d_16(data = master_list$UNASR17[[1]],master_list$UNASR17[[2]])
cohorts18<-f_d_16(data = master_list$UNASR18[[1]],master_list$UNASR18[[2]])
cohorts19<-f_d_16(data = master_list$UNASR19[[1]],master_list$UNASR19[[2]])
cohorts20<-f_d_16(data = master_list$UNSR2020,master_list$UNASR2020)

```

```{r}
a<- rbind(c(cohorts16$w_n_list,cohorts17$w_n_list[[1]] )) 
```
```{r}
# Now to pool and impute the data

POOLED<- base::rbind(master_list$UNASR16[[1]]$data,master_list$UNASR17[[1]], master_list$UNASR18[[1]], master_list$UNASR19[[1]]) 


imp_data<- mice(POOLED, predictorMatrix = quickpred(POOLED, exclude= c("hhid", "Weight_household","ORIGIN","MARSTAT", "Foodstamps", "TANF", "RCA", "SSI", "GA","Miscash", "PubHo", "NUM_PROGS")),m = 21)

```
#### making the pooled and weighted dataset
```{r}
POOLED<- base::rbind(master_list$UNASR16[[2]]$data,master_list$UNASR17[[2]], master_list$UNASR18[[2]], master_list$UNASR19[[2]], master_list$UNSR2020) 

wPOOLED<- svydesign(ids=~hhid, weights =~Weight_household,data = POOLED)
```

```{r, echo=FALSE}
impPOOLED<- mice(POOLED, predictorMatrix = quickpred(POOLED, exclude= c("hhid", "Weight_household","ORIGIN","MARSTAT", "Foodstamps", "TANF", "RCA", "GA","Miscash", "PubHo", "NUM_PROGS", "TILLJOB", "TILLJOBb")),m = 21)

```

## Need a funcation to do DESC on every variable 
```{r}
Desc(POOLED)

```

# Descriptive Statistics
## Pre-Migration Economic Sector
```{r error=TRUE}
library(DescTools)
Desc(temp16$ECOSECTOR)
Desc(temp17$ECOSECTOR)
Desc(temp18$ECOSECTOR)
Desc(POOLED$ECOSECTOR)
```


## Working Hours


```{r}
summary(temp16$WEEKHOUR)
summary(temp17$WEEKHOUR)
summary(temp18$WEEKHOUR)
```
##Region of Resettlment

```{r error=TRUE}
Desc(temp16$HOSTREG)

Desc(temp17$HOSTREG)

Desc(temp18$HOSTREG)

Desc(POOLED$HOSTREG)

```

## National Origin
```{r}

Freq(temp16$ORIGIN)
Freq(temp17$ORIGIN)
Freq(temp18$ORIGIN)
Freq(POOLED$ORIGIN)
```

## Current Enrollement in English Training Programs

```{R}
Freq(temp16$CURENGEN)

Freq(temp17$CURENGEN)

Freq(temp18$CURENGEN)

Freq(POOLED$CURENGEN)

```

## Current Enrollement in Employment training programs


```{r}
Freq(temp16$CUREMPT)
Freq(temp17$CUREMPT)
Freq(temp18$CUREMPT)
Freq(POOLED$CUREMPT)

```

## Current English Proficiency

```{r}
Freq(temp16$CURENG)
Freq(temp17$CURENG)
Freq(temp18$CURENG)
Freq(POOLED$CURENG)
sd(as.numeric(POOLED$CURENG), na.rm=T)
```

## Sex

```{r}

Freq(temp16$SEX)
Freq(temp17$SEX)
Freq(temp18$SEX)
Freq(POOLED$SEX)
```

## Marital Status

```{r}
Freq(temp16$MARSTAT)

Freq(temp17$MARSTAT)

Freq(temp18$MARSTAT)

Freq(POOLED$MARSTAT)
```

## Number of Dependents in household

```{r}
summary(temp16$DEPENDS)
sd(temp16$DEPENDS)
summary(temp17$DEPENDS)
sd(temp17$DEPENDS)
summary(temp18$DEPENDS)
sd(temp18$DEPENDS)
summary(POOLED$DEPENDS)
sd(POOLED$DEPENDS)

```

## Years of EDUC_YEARSation

```{r}
summary(temp16$HIGHEST_DEGREE)
sd(temp16$HIGHEST_DEGREE, na.rm=T)
```
## Context Variable   
```{r}
summary(temp16$CONTEXT)
sd(temp16$CONTEXT, na.rm= T)

summary(temp17$CONTEXT)
sd(temp17$CONTEXT, na.rm= T)

summary(temp18$CONTEXT)
sd(temp18$CONTEXT, na.rm= T)

summary(POOLED$CONTEXT)
sd(POOLED$CONTEXT, na.rm= T)
```

## PreMigration English Proficiency


```{r}

summary(temp16$PREENG)
summary(temp16$CURENG)
```

# Analysis with the imputed models

##First FI Pooled "Basics" Nest
```{r}
basicsPOOLED<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS, family = "binomial",design = wPOOLED))
BPoolpool<-pool(basicsPOOLED)
summary(BPoolpool)
```




## Second Pre Context Nest
```{r}
pcpool<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,ref="Iraq")+relevel(ECOSECTOR, "Other"), family = "binomial",design =wPOOLED ))
preconPOOLED<- pool(pcpool)
summary(preconPOOLED)
```


## Third Post Context Nest
```{r}
pocopool<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,ref="Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR, family = "binomial", design = wPOOLED))
posconPOOLED<- pool(pocopool)
summary(posconPOOLED)
```


## Fourth, Add Pre-Human Capital Vars
```{r}

prehupool<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,ref="Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+HIGHEST_DEGREE+CONTEXT+PREENG , family = "binomial", design = wPOOLED))
prehuPOOLED<- pool(prehupool)
summary(prehuPOOLED)
```


#Fith, the Final Model (Use this model for intra-model prediction comparisons)
```{r}

pohupool<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,ref="Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+HIGHEST_DEGREE+CONTEXT+PREENG+CURENGEN+CUREMPT+CURENG+relevel(URECOSEC, ref=2)+TILLJOBb+WEEKHOUR , family = "binomial", design =  wPOOLED ))
posthuPOOLED<- pool(pohupool)
a<-summary(posthuPOOLED)
```
## Comparing Results with unimputed data
```{r}
unweighted_POOLED_ES<-svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN, ref="Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+HIGHEST_DEGREE+PREENG+CURENGEN+CUREMPT+CURENG+relevel(URECOSEC, ref=2)+TILLJOBb+WEEKHOUR , family = "binomial", design = wPOOLED)

unweighted_POOLED_ES$aic
```
## What about factorizing survey year?
```{r}

pohupool<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+relevel(factor(SVYYR), ref = "2016")+HIGHEST_DEGREE+PREENG+CURENGEN+CUREMPT+CURENG+relevel(URECOSEC, ref=2)+TILLJOB+WEEKHOUR , family = "binomial", design = wPOOLED))
posthuPOOLED<- pool(pohupool)
summary(posthuPOOLED)
```


##Making the prediction dataframe.
### AIC AND BIC

```{r}
#comparing AIC's in both models I already have the context +Basics model
posconPOOLED$glanced
POOLED$URECOSEC<-relevel(POOLED$URECOSEC, ref=2)
#making the basics+human capital model
compareFIpool<- with(impPOOLED, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+HIGHEST_DEGREE+PREENG+CURENGEN+CUREMPT+CURENG+URECOSEC+TILLJOBb , family = "binomial", design = wPOOLED))
compareFIHCPOOLED<- pool(compareFIpool)
compareFIHCPOOLED$glanced
#The human capital one has the lower AIC and BIC
```

### Non-Miced predictions
```{r}

POOLED$URECOSEC<-relevel(POOLED$URECOSEC, ref=2)
modela <- svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+HIGHEST_DEGREE+PREENG+CURENGEN+CUREMPT+CURENG+relevel(URECOSEC, ref=2)+TILLJOB+WEEKHOUR , family = "binomial", design = wPOOLED)

summary(modela)
#Making the hypothetical dataframe for a maximally advantaged contextual person. 
maxconpred <- data.frame(RESIDENCY=factor(3), SEX="Male", AGE=39.7, numppl=3, MARSTAT="Never Married", TILLJOB=1, HIGHEST_DEGREE=12, ECOSECTOR="Professional", URECOSEC="Retail/Sales", ORIGIN="Cuba", PREENG="Not Well", HOSTREG="South", CURENGEN="No", CUREMPT="No", CURENG="Well", DEPENDS=1, SVYYR=2018, WEEKHOUR=38.33, TILLJOBb=1)


maxhumpred <- data.frame(RESIDENCY=factor(3), SEX="Male", AGE=39.7, numppl=3, MARSTAT="Never Married", TILLJOB=1, HIGHEST_DEGREE=20, ECOSECTOR="Other", URECOSEC= "Professional/ED/Health/SocialServices", ORIGIN="Iraq", PREENG="Very Well", HOSTREG="West", CURENGEN="No", CUREMPT="No", CURENG="Very Well", DEPENDS=1, SVYYR=2016, WEEKHOUR=38.33, TILLJOBb=1)
#NEED to Add KIDS to make predictions
#predict(modela, newdata =maxconpred, type = "response")

#predict(modela, newdata =maxhumpred, type = "response")
```


#2016 Fith, the Final Model (Use this model for intra-model prediction comparisons)
```{r}

pohu19<- with(imp19, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+HOSTREG+HIGHEST_DEGREE+CONTEXT+PREENG+ CURENGEN+CUREMPT+CURENG+relevel(URECOSEC, ref=2)+ TILLJOBb+WEEKHOUR , family = "binomial", design = wtemp19))
posthu19<- pool(pohu19)
summary(posthu19)
```

# 2017 FI Models 
## Basicis Model
```{r}
basics17<- with(imp17, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS, family = "binomial",design = wtemp17))
B17pool<-pool(basics17)
summary(B17pool)


```

## Second Pre Context Nest
```{r}
pc17<- with(imp17, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other"), family = "binomial",design =wtemp17 ))
precon17<- pool(pc17)
summary(precon17)
```

## Third Post Context Nest
```{r}
poco17<- with(imp17, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR, family = "binomial", design = wtemp17))
poscon17<- pool(poco17)
summary(poscon17)
```

## Fourth, Add Pre-Human Capital Vars
```{r}

prehu17<- with(imp17, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+HIGHEST_DEGREE+CONTEXT+PREENG , family = "binomial", design = wtemp17))
prehu17<- pool(prehu17)
summary(prehu17)

```

#Fith, the Final Model (Use this model for intra-model prediction comparisons)
```{r}

pohu17<- with(imp17, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+HOSTREG+relevel(URECOSEC, ref=2)+HIGHEST_DEGREE+CONTEXT+relevel(ECOSECTOR, "Other")+PREENG+ CURENGEN+CUREMPT+CURENG+ TILLJOBb+WEEKHOUR , family = "binomial", design = wtemp17))
posthu17<- pool(pohu17)
summary(posthu17)
```

# 2018 FI Models 
## Basicis Model
```{r}
basics18<- with(imp18, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS, family = "binomial",design = wtemp18))
B18pool<-pool(basics18)
summary(B18pool)


```

## Second Pre Context Nest
```{r}
pc18<- with(imp18, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other"), family = "binomial",design =wtemp18 ))
precon18<- pool(pc18)
summary(precon18)
```

## Third Post Context Nest
```{r}
poco18<- with(imp18, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR, family = "binomial", design = wtemp18))
poscon18<- pool(poco18)
summary(poscon18)
```

## Fourth, Add Pre-Human Capital Vars
```{r}

prehu18<- with(imp18, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+HIGHEST_DEGREE+CONTEXT+PREENG , family = "binomial", design = wtemp18))
prehu18<- pool(prehu18)
summary(prehu18)

```

#Fith, the Final Model (Use this model for intra-model prediction comparisons)
```{r}

pohu18<- with(imp18, svyglm(FI~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+HOSTREG+relevel(URECOSEC, ref=2)+HIGHEST_DEGREE+CONTEXT+relevel(ECOSECTOR, "Other")+PREENG+ CURENGEN+CUREMPT+CURENG+ TILLJOBb+WEEKHOUR , family = "binomial", design = wtemp18))
posthu18<- pool(pohu18)
summary(posthu18)
```

#  TIme to First Job 

## First Pooled "Basics" Nest
```{r}
basicsTJPOOLED<- with(impPOOLED, svyglm(TILLJOB~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS, family = "binomial",design = wPOOLED))
BPoolTJpool<-pool(basicsTJPOOLED)
summary(BPoolTJpool)
```


## Second Pre Context Nest
```{r}
pcTJpool<- with(impPOOLED,svyglm(TILLJOB~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+relevel(ORIGIN,"Iraq" )+relevel(ECOSECTOR,"Other"), family = "binomial",design =wPOOLED ))
preconTJPOOLED<- pool(pcTJpool)
summary(preconTJPOOLED)
```


## Third Post Context Nest
```{r}
pocoTJpool<- with(impPOOLED, svyglm(TILLJOB~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+relevel(ORIGIN,"Iraq")+relevel(ECOSECTOR,ref = "Other")+HOSTREG+SVYYR, family = "binomial", design = wPOOLED))
posconTJPOOLED<- pool(pocoTJpool)
summary(posconTJPOOLED)
```


## Fourth, Add Pre-Human Capital Vars (Final? because Till job may be before current variables)
```{r}
prezhuTJpool<- with(impPOOLED, svyglm(TILLJOB~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+relevel(ORIGIN,"Iraq")+relevel(ECOSECTOR,"Other")+HOSTREG+SVYYR+HIGHEST_DEGREE+PREENG, family = "binomial", design = wPOOLED))
prezhuTJPOOLED<- pool(prezhuTJpool)
summary(prezhuTJPOOLED)

```

## Firth, the final model
```{r}

prehuTJpool<- with(impPOOLED, svyglm(TILLJOB~ as.numeric(RESIDENCY)+ SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+relevel(ORIGIN,"Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+HIGHEST_DEGREE+CONTEXT+PREENG+CURENGEN:PREENG+CUREMPT+CURENG, family = "binomial", design = wPOOLED))
prehuTJPOOLED<- pool(prehuTJpool)
summary(prehuTJPOOLED)
```

```{r}
#Supplemantal Models
TJ_pooled_unmiced<-svyglm(TILLJOB~ as.numeric(RESIDENCY)+ SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+relevel(ORIGIN,"Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+EDUC+CONTEXT+PREENG+CURENGEN+CUREMPT+CURENG, family = "binomial", design = wPOOLED)
summary(TJ_pooled_unmiced)
TJ_pooled_unmiced
#2016
summary(svyglm(TILLJOB~ as.numeric(RESIDENCY)+ SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,"Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+HIGHEST_DEGREE+CONTEXT+PREENG+CURENGEN+CUREMPT+CURENG, family = "binomial", design = wtemp16))

#2017
summary(svyglm(TILLJOB~ as.numeric(RESIDENCY)+ SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,"Iraq")+relevel(ECOSECTOR, "Other")+HOSTREG+HIGHEST_DEGREE+CONTEXT+PREENG+CURENGEN+CUREMPT+CURENG, family = "binomial", design = wtemp17))

#2018 #have to take out Pre=EcoSector because no variation. This is also true for the 2019 model. 
summary(svyglm(TILLJOB~ as.numeric(RESIDENCY)+ SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,"Iraq")++HOSTREG+HIGHEST_DEGREE+CONTEXT+PREENG+CURENGEN+CUREMPT+CURENG, family = "binomial", design = wtemp18))


#2019
summary(svyglm(TILLJOB~ as.numeric(RESIDENCY)+ SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+relevel(ORIGIN,"Iraq")+HOSTREG+HIGHEST_DEGREE+CONTEXT+PREENG+CURENGEN+CUREMPT+CURENG, family = "binomial", design = wtemp19))
```

# The comparisons between contexts and human capital
```{r}
posconTJPOOLED$glanced

compareTJpool<- with(impPOOLED, svyglm(TILLJOB~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+HIGHEST_DEGREE+PREENG+CURENGEN+CUREMPT+CURENG+URECOSEC , family = "binomial", design = wPOOLED))
compareTJHCPOOLED<- pool(compareTJpool)
compareTJHCPOOLED$glanced
## Contexts are better at the AIC and BIC measures, but what about Predicted probabilities?
```
### PRedicted Probabilities
```{r}
modelb <- svyglm(TILLJOB~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+HIGHEST_DEGREE+PREENG+CURENGEN+CUREMPT+CURENG+URECOSEC+TILLJOBb , family = "binomial", design = wPOOLED)


#Making the hypothetical dataframe for a maximally advantaged contextual person. 
maxconpred <- data.frame(RESIDENCY=factor(3), SEX="Male", AGE=39.7, numppl=3, MARSTAT="Never Married", TILLJOB=1, HIGHEST_DEGREE=12, ECOSECTOR="Professional", URECOSEC="Retail/Sales", ORIGIN="Cuba", PREENG="Not Well", HOSTREG="South", CURENGEN="No", CUREMPT="No", CURENG="Well", DEPENDS=1, KIDS=1, SVYYR=2018, WEEKHOUR=38.33, TILLJOBb=1)


maxhumpred <- data.frame(RESIDENCY=factor(3), SEX="Male", AGE=39.7, numppl=3, MARSTAT="Never Married", TILLJOB=1, HIGHEST_DEGREE=20, ECOSECTOR="Other", URECOSEC= "Professional/ED/Health/SocialServices", ORIGIN="Iraq", PREENG="Very Well", HOSTREG="West", CURENGEN="No", CUREMPT="No", CURENG="Very Well", DEPENDS=1, KIDS=1, SVYYR=2016, WEEKHOUR=38.33, TILLJOBb=1)

predict(modelb, newdata =maxconpred, type = "response")

predict(modelb, newdata =maxhumpred, type = "response")
```
# Log of Weekly Working Hours

##First FI Pooled "Basics" Nest
```{r}
WHbasicsPOOLED<- with(impPOOLED, svyglm(log(WEEKHOUR +1089/40) ~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS,design = wPOOLED))
WHBPoolpool<-pool(WHbasicsPOOLED)
summary(WHBPoolpool)
```




## Second Pre Context Nest
```{r}
WHpcpool<- with(impPOOLED, svyglm(log(WEEKHOUR +1089/40)~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other"),design =wPOOLED ))
WHpreconPOOLED<- pool(WHpcpool)
summary(WHpreconPOOLED)
```


## Third Post Context Nest
```{r}
WHpocopool<- with(impPOOLED, svyglm(log(WEEKHOUR +1089/40)~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR, design = wPOOLED))
WHposconPOOLED<- pool(WHpocopool)
summary(WHposconPOOLED)
```


## Fourth, Add Pre-Human Capital Vars
```{r}

WHprehupool<- with(impPOOLED, svyglm(log(WEEKHOUR +1089/40)~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+HIGHEST_DEGREE+CONTEXT+PREENG, design = wPOOLED))
WHprehuPOOLED<- pool(WHprehupool)
summary(WHprehuPOOLED)

```



#Fith, the Final Model (Use this model for intra-model prediction comparisons)
```{r}

WHpohupool<- with(impPOOLED, svyglm(log(WEEKHOUR +1089/40)~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+ORIGIN+relevel(ECOSECTOR, "Other")+HOSTREG+SVYYR+HIGHEST_DEGREE+CONTEXT+PREENG+CURENGEN+CUREMPT+CURENG+relevel(URECOSEC, ref=2)+TILLJOB+FI, design = wPOOLED))
WHposthuPOOLED<- pool(WHpohupool)
summary(WHposthuPOOLED)

```


# Comparing weekly working hours across maximal individuals

```{r}
WHposconPOOLED$glanced

compareWHpool<- with(impPOOLED, svyglm(log(WEEKHOUR +1089/40)~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+HIGHEST_DEGREE+PREENG+CURENGEN+CUREMPT+CURENG+URECOSEC+TILLJOBb, design = wPOOLED))
compareWHHCPOOLED<- pool(compareWHpool)
compareWHHCPOOLED$glanced
## Contexts are better at the AIC and BIC measures, but what about Predicted probabilities?

```



```{r}
modelc <- svyglm(log(WEEKHOUR +1089/40)~ as.numeric(RESIDENCY)+SEX+AGE+(AGE^2)+numppl+MARSTAT+DEPENDS+KIDS+HIGHEST_DEGREE+PREENG+CURENGEN+CUREMPT+CURENG+URECOSEC+TILLJOBb, design = wPOOLED)


#Making the hypothetical dataframe for a maximally advantaged contextual person. 
maxconpred <- data.frame(RESIDENCY=factor(3), SEX="Male", AGE=39.7, numppl=3, MARSTAT="Never Married", KIDS=1, TILLJOB=1, HIGHEST_DEGREE=12, ECOSECTOR="Professional", URECOSEC="Retail/Sales", ORIGIN="Cuba", PREENG="Not Well", HOSTREG="South", CURENGEN="No", CUREMPT="No", CURENG="Well", DEPENDS=1, SVYYR=2018, WEEKHOUR=38.33, TILLJOBb=1)


maxhumpred <- data.frame(RESIDENCY=factor(3), SEX="Male", AGE=39.7, numppl=3, MARSTAT="Never Married", KIDS=1, TILLJOB=1, HIGHEST_DEGREE=20, ECOSECTOR="Other", URECOSEC= "Professional/ED/Health/SocialServices", ORIGIN="Iraq", PREENG="Very Well", HOSTREG="West", CURENGEN="No", CUREMPT="No", CURENG="Very Well", DEPENDS=1, SVYYR=2016, WEEKHOUR=38.33, TILLJOBb=1)

predict(modelc, newdata =maxconpred, type = "response")

predict(modelc, newdata =maxhumpred, type = "response")

```

# The Group-by Descriptive I need

```{r}
result <- UNSR17 %>%
  group_by(RESIDENCY, ui_soi_pubassist) %>%
  summarise(count = n()) %>%
  mutate(percent = count / sum(count) * 100)
print(result)
```
# For Canadian Comparisons
I need to find the proportion of economically self-sufficient refugees in each American cohort. They need to be weighted. 

```{r}
USin19cohort14<- UNSR19[UNSR19$RESIDENCY==2014,]
USin19cohort14<- USin19cohort14[!(is.na(USin19cohort14$hhid)),]
USin19cohort14_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin19cohort14,na.rm=T)
svymean(USin19cohort14$FI, USin19cohort14_w, na.rm=T)
```
Now for USin19cohort15
```{r}
USin19cohort15<- UNSR19[UNSR19$RESIDENCY==2015,]
USin19cohort15<- USin19cohort15[!(is.na(USin19cohort15$hhid)),]
USin19cohort15_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin19cohort15,na.rm=T)
USin19cohort15$FI
```
```{r}
USin19cohort16<- UNSR19[UNSR19$RESIDENCY==2016,]
USin19cohort16<- USin19cohort16[!(is.na(USin19cohort16$hhid)),]
USin19cohort16_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin19cohort16,na.rm=T)
USin19cohort16$FI
```
```{r}
USin19cohort17<- UNSR19[UNSR19$RESIDENCY==2017,]
USin19cohort17<- USin19cohort17[!(is.na(USin19cohort17$hhid)),]
USin19cohort17_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin19cohort17,na.rm=T)
USin19cohort17$FI
```
```{r}
USin19cohort18<- UNSR19[UNSR19$RESIDENCY==2018,]
USin19cohort18<- USin19cohort18[!(is.na(USin19cohort18$hhid)),]
USin19cohort18_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin19cohort18,na.rm=T)
USin19cohort18$FI
```
Now for the 2018.
```{r}
USin18cohort17<- UNSR18[UNSR18$RESIDENCY==2017,]
USin18cohort17<- USin18cohort17[!(is.na(USin18cohort17$hhid)),]
USin18cohort17_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin18cohort17,na.rm=T)
USin18cohort17$FI
```
```{r}
USin18cohort16<- UNSR18[UNSR18$RESIDENCY==2016,]
USin18cohort16<- USin18cohort16[!(is.na(USin18cohort16$hhid)),]
USin18cohort16_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin18cohort16,na.rm=T)
USin18cohort16$FI
```
```{r}
USin18cohort15<- UNSR18[UNSR18$RESIDENCY==2015,]
USin18cohort15<- USin18cohort15[!(is.na(USin18cohort15$hhid)),]
USin18cohort15_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin18cohort15,na.rm=T)
USin18cohort15$FI
```
```{r}
USin18cohort14<- UNSR18[UNSR18$RESIDENCY==2014,]
USin18cohort14<- USin18cohort14[!(is.na(USin18cohort14$hhid)),]
USin18cohort14_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin18cohort14,na.rm=T)
USin18cohort14$FI
```
```{r}
USin18cohort13<- UNSR18[UNSR18$RESIDENCY==2013,]
USin18cohort13<- USin18cohort13[!(is.na(USin18cohort13$hhid)),]
USin18cohort13_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin18cohort13,na.rm=T)
USin18cohort13$FI
```
Now for 2017

```{r}
USin17cohort16<- UNSR17[UNSR17$RESIDENCY==2016,]
USin17cohort16<- USin17cohort16[!(is.na(USin17cohort16$hhid)),]
USin17cohort16_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin17cohort16,na.rm=T)
svymean(USin17cohort16$FI, USin17cohort16_w, na.rm=T)
```
```{r}
USin17cohort15<- UNSR17[UNSR17$RESIDENCY==2015,]
USin17cohort15<- USin17cohort15[!(is.na(USin17cohort15$hhid)),]
USin17cohort15_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin17cohort15,na.rm=T)
svymean(USin17cohort15$FI, USin17cohort15_w, na.rm=T)
```

```{r}
USin17cohort14<- UNSR17[UNSR17$RESIDENCY==2014,]
USin17cohort14<- USin17cohort14[!(is.na(USin17cohort14$hhid)),]
USin17cohort14_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin17cohort14,na.rm=T)
svymean(USin17cohort14$FI, USin17cohort14_w, na.rm=T)
```

```{r}
USin17cohort13<- UNSR17[UNSR17$RESIDENCY==2013,]
USin17cohort13<- USin17cohort13[!(is.na(USin17cohort13$hhid)),]
USin17cohort13_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin17cohort13,na.rm=T)
svymean(USin17cohort13$FI, USin17cohort13_w, na.rm=T)
```

```{r}
USin17cohort12<- UNSR17[UNSR17$RESIDENCY==2012,]
USin17cohort12<- USin17cohort12[!(is.na(USin17cohort12$hhid)),]
USin17cohort12_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin17cohort12,na.rm=T)
svymean(USin17cohort12$FI, USin17cohort12_w, na.rm=T)
```
And 2016

```{r}
USin16cohort15<- UNSR16[UNSR16$RESIDENCY==2015,]
USin16cohort15<- USin16cohort15[!(is.na(USin16cohort15$hhid)),]
USin16cohort15_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin16cohort15,na.rm=T)
svymean(USin16cohort15$FI, USin16cohort15_w, na.rm=T)
```
```{r}
USin16cohort14<- UNSR16[UNSR16$RESIDENCY==2014,]
USin16cohort14<- USin16cohort14[!(is.na(USin16cohort14$hhid)),]
USin16cohort14_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin16cohort14,na.rm=T)
svymean(USin16cohort14$FI, USin16cohort14_w, na.rm=T)
```
```{r}
USin16cohort13<- UNSR16[UNSR16$RESIDENCY==2013,]
USin16cohort13<- USin16cohort13[!(is.na(USin16cohort13$hhid)),]
USin16cohort13_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin16cohort13,na.rm=T)
svymean(USin16cohort13$FI, USin16cohort13_w, na.rm=T)
```
```{r}
USin16cohort12<- UNSR16[UNSR16$RESIDENCY==2012,]
USin16cohort12<- USin16cohort12[!(is.na(USin16cohort12$hhid)),]
USin16cohort12_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin16cohort12,na.rm=T)
svymean(USin16cohort12$FI, USin16cohort12_w, na.rm=T)
```
```{r}
USin16cohort11<- UNSR16[UNSR16$RESIDENCY==2011,]
USin16cohort11<- USin16cohort11[!(is.na(USin16cohort11$hhid)),]
USin16cohort11_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin16cohort11,na.rm=T)
svymean(USin16cohort11$FD, USin16cohort11_w, na.rm=T)
```

# Now to seperate them male and female headed households (and use prettier and more consice code.)

```{r}
USin16cohort11<- UNSR16[UNSR16$RESIDENCY==2011 & UNSR16$SEX=="Male",]
USin16cohort11<- USin16cohort11[!(is.na(USin16cohort11$hhid)),]
USin16cohort11_w<- svydesign(ids=~hhid, weights =~Weight_household,data = USin16cohort11,na.rm=T)
svymean(USin16cohort11$FD, USin16cohort11_w, na.rm=T)
```





